### 2021-01-11 draft.tex
Initial Overleaf Import

\documentclass{sigchi}

% Use this section to set the ACM copyright statement (e.g. for
% preprints).  Consult the conference website for the camera-ready
% copyright statement.

% Copyright
\CopyrightYear{2021}
%\setcopyright{acmcopyright}
\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}
% DOI
\doi{https://doi.org/10.1145/3313831.XXXXXXX}
% ISBN
\isbn{XXX-X-XXXX-XXXX-X/21/05}
%Conference
\conferenceinfo{CHI'21,}{May 8--13, 2021, Yokohama, Japan}
%Price
%\acmPrice{\$15.00}

% Use this command to override the default ACM copyright statement
% (e.g. for preprints).  Consult the conference website for the
% camera-ready copyright statement.

%% HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP --
%% Please note you need to make sure the copy for your specific
%% license is used here!
% \toappear{
% Permission to make digital or hard copies of all or part of this work
% for personal or classroom use is granted without fee provided that
% copies are not made or distributed for profit or commercial advantage
% and that copies bear this notice and the full citation on the first
% page. Copyrights for components of this work owned by others than ACM
% must be honored. Abstracting with credit is permitted. To copy
% otherwise, or republish, to post on servers or to redistribute to
% lists, requires prior specific permission and/or a fee. Request
% permissions from \href{mailto:Permissions@acm.org}{Permissions@acm.org}. \\
% \emph{CHI '16},  May 07--12, 2016, San Jose, CA, USA \\
% ACM xxx-x-xxxx-xxxx-x/xx/xx\ldots \$15.00 \\
% DOI: \url{http://dx.doi.org/xx.xxxx/xxxxxxx.xxxxxxx}
% }

% Arabic page numbers for submission.  Remove this line to eliminate
% page numbers for the camera ready copy
% \pagenumbering{arabic}

% Load basic packages
\usepackage{balance}       % to better equalize the last page
\usepackage{graphics}      % for EPS, load graphicx instead 
\usepackage[T1]{fontenc}   % for umlauts and other diaeresis
\usepackage{txfonts}
\usepackage{mathptmx}
\usepackage[pdflang={en-US},pdftex]{hyperref}
\usepackage{color}
\usepackage{booktabs}
\usepackage{textcomp}
\usepackage{lipsum}

% Some optional stuff you might like/need.
\usepackage{microtype}        % Improved Tracking and Kerning
% \usepackage[all]{hypcap}    % Fixes bug in hyperref caption linking
\usepackage{ccicons}          % Cite your images correctly!
% \usepackage[utf8]{inputenc} % for a UTF8 editor only

% If you want to use todo notes, marginpars etc. during creation of
% your draft document, you have to enable the "chi_draft" option for
% the document class. To do this, change the very first line to:
% "\documentclass[chi_draft]{sigchi}". You can then place todo notes
% by using the "\todo{...}"  command. Make sure to disable the draft
% option again before submitting your final document.
\usepackage{todonotes}

% Paper metadata (use plain text, for PDF inclusion and later
% re-using, if desired).  Use \emtpyauthor when submitting for review
% so you remain anonymous.
\def\plaintitle{Lifestyle and study equipment changes during distance learning}
\def\plainauthor{First Author, Second Author, Third Author,
  Fourth Author, Fifth Author, Sixth Author}
\def\emptyauthor{}
\def\plainkeywords{distance learning; study environment; work environment; motivation; pandemic;}
\def\plaingeneralterms{Documentation, Standardization}

% llt: Define a global style for URLs, rather that the default one
\makeatletter
\def\url@leostyle{%
  \@ifundefined{selectfont}{
    \def\UrlFont{\sf}
  }{
    \def\UrlFont{\small\bf\ttfamily}
  }}
\makeatother
\urlstyle{leo}

% To make various LaTeX processors do the right thing with page size.
\def\pprw{8.5in}
\def\pprh{11in}
\special{papersize=\pprw,\pprh}
\setlength{\paperwidth}{\pprw}
\setlength{\paperheight}{\pprh}
\setlength{\pdfpagewidth}{\pprw}
\setlength{\pdfpageheight}{\pprh}

% Make sure hyperref comes last of your loaded packages, to give it a
% fighting chance of not being over-written, since its job is to
% redefine many LaTeX commands.
\definecolor{linkColor}{RGB}{6,125,233}
\hypersetup{%
  pdftitle={\plaintitle},
% Use \plainauthor for final version.
%  pdfauthor={\plainauthor},
  pdfauthor={\emptyauthor},
  pdfkeywords={\plainkeywords},
  pdfdisplaydoctitle=true, % For Accessibility
  bookmarksnumbered,
  pdfstartview={FitH},
  colorlinks,
  citecolor=black,
  filecolor=black,
  linkcolor=black,
  urlcolor=linkColor,
  breaklinks=true,
  hypertexnames=false
}

% create a shortcut to typeset table headings
% \newcommand\tabhead[1]{\small\textbf{#1}}

% End of preamble. Here it comes the document.
\begin{document}

\title{\plaintitle}

\numberofauthors{3}
\author{%
  \alignauthor{Author One\\
    \affaddr{for Submission}\\
    \affaddr{}\\
    \email{}}\\
  \alignauthor{Author Two\\
    \affaddr{for Submission}\\
    \affaddr{}\\
    \email{}}\\
  \alignauthor{Author Three\\
    \affaddr{for Submission}\\
    \affaddr{}\\
    \email{}}\\
  \alignauthor{Author Four\\
    \affaddr{for Submission}\\
    \affaddr{}\\
    \email{}}\\
}

\maketitle

\begin{abstract}
Given the appearance of the new pathological risk incurred during the 2020 Covid-19 pandemic, most educational institutions, be them either lower or higher educational, have had to restrict their activity on-campus and promote a fully online pedagogical methodology in order to avoid the spread of the virus and protect the health of both students and teachers. By employing already existing software solutions to the likes of \emph{Zoom}, \emph{Microsoft Teams}, and other existing tools, courses have been completely moved within the realm of the internet to the best of the ability of each educational institution. In this context, the authors are trying to investigate the effects that the sudden move to distance learning has had on students from different backgrounds, as well as how they have been forced to change their study and work environment to cope with the perpetual stress of academic life within the confines of their own home.
\end{abstract}

% ACM Classfication

\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10003456.10003457.10003527.10003542</concept_id>
<concept_desc>Social and professional topics~Adult education</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003120.10003121</concept_id>
<concept_desc>Human-centered computing~Human computer interaction (HCI)</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003120.10003121.10003122.10003334</concept_id>
<concept_desc>Human-centered computing~User studies</concept_desc>
<concept_significance>100</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Social and professional topics~Adult education}
\ccsdesc[300]{Human-centered computing~Human computer interaction (HCI)}
\ccsdesc[100]{Human-centered computing~User studies}

% Author Keywords
\keywords{\plainkeywords}

% Print the classification codes
\printccsdesc

\section{Introduction}

At the start of 2020, most countries around the world have had to impose strict restriction upon public spaces and institution in order to combat the eventual spread of Covid-19 within their populations\cite{fauci_lane_redfield_2020}. One measure imposed upon the educational systems was to forbid as much as possible lectures and other educational activities within their campuses as to avoid unnecessary and possible life-threatening contact between members of the institutions. In order to continue with the already started semester, most if not all education institutions have put forward online procedures based on already existing infrastructure in order for courses to still take place. Students have suddenly found themselves studying full time from the comfort of their home, not needing to travel to the universities campuses anymore. During their own experiences as students within the Summer 2020 semester, the authors have notice certain trends within their own behaviour and that of fellow students related to the unpreparedness of their own home-study environment and the rising motivational issues, and so, decided to perform an inquiry under the course work for the User Research Methods PR at the Technical University of Vienna, in order to investigate if indeed there was a general unpreparedness across the student population for such a drastic move to distance learning, as well as, if there is such a notion as a \emph{perfect study environment}, and in the end, conclude with a small \emph{tips and tricks} handbook which other students might find helpful in order to increase their comfort and motivation for studying at home and eventually decrease the amount of stress cause by social isolation.\cite{hossain_mental_2020}

\section{Related Work}

Here we should probably talk about the previous papers we read about distance learning, social isolation, education during other pandemics, as well as papers about the research methodologies

\section{Methods}

\subsubsection{Research Questions}
Before starting the

\subsubsection{Methodologies}
In order to perform their research as best as possible, the authors have decided on utilizing three separate methodologies in order to achieve a coherent approach and take into account as many aspects related towards \emph{study environments} as possible. They started by performing auto-ethnography upon themselves to have an introspective look over their own experience during the first and second semesters of their studies within the context of the pandemic restrictions. Using the findings of the auto-ethnography, they have arrived at a number of interview questions that where used in a series of semi-structured interviews with participants outside of the research team. Ending by performing an photographic ethnography of pictures taken by the same interview participants in order to analyse them in parallel with the interview transcriptions and achieve a more coherent image of each participants actual study environments.

\subsection{Auto-ethnography}

Before starting the auto-ethnography research, each researcher has been given an information sheet and consent form which had to be sign by the research-participant and one of the other researchers. The structure of the document has been agreed upon unanimously by the team as so to avoid any potential issues related to data privacy of the resulting documents from the auto-ethnographic research.
After signing the consent form, each researcher has had to conduct an inner-inquiry upon his or hers experience that resulted from the drastic change towards full-time studying from home, as well as making a comparison between their study/work environment and study workload between their previous semester (e.g. Winter 2019/2020) and the next restricted semesters (e.g. Summer 2020, Winter 2020/2021).
Upon finishing there report about their own experience, each researcher had to take a picture of their current study environment/s (see Figure~\ref{fig:figure1} as an example) and attach it to the report. Afterwards all reports where analysed by each researcher, and researcher-participant had to perform a presentation of their experience to all other researchers. Findings culminating in organizing the information from a constructionist approach using Miro\footnote{\url{https://miro.com/}} and extracting possible interview questions for their findings. After having decided on the possible interview questions, sample semi-structured interview took place, having one of the researchers as a participant, and two others as interviewer and observer. Upon finishing the sample interview, the interview question had been filtered to only five central questions as so to provide a structure for the incoming participant interviews.

\begin{figure}
\centering
  \includegraphics[width=0.9\columnwidth]{figures/auto-e-picture}
  \caption{Sample picture from the Auto-Ethnographic method, showing the desk of one of the researchers}~\label{fig:figure1}
\end{figure}

\subsection{Semi-structured Interviews}

\subsection{Photographic Ethnography}

\section{Findings}

\section{Discussion}

\section{Implications for design}

\section{Conclusions and future work}

\section{Acknowledgments}
Thank you to all our interview participants for taking their time off their studies and work in order to help us with this assignment. Thank you to TU Wien for giving us access to the needed tools in order to prepare the assignment,  \textit{as good as they are}. No other funding was provided.

% REFERENCES FORMAT
% References must be the same font size as other body text.
\bibliographystyle{SIGCHI-Reference-Format}
\bibliography{sample}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2021-01-11 proceedings.tex
Initial Overleaf Import

\documentclass{sigchi}

% Use this section to set the ACM copyright statement (e.g. for
% preprints).  Consult the conference website for the camera-ready
% copyright statement.

% Copyright
\CopyrightYear{2020}
%\setcopyright{acmcopyright}
\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}
% DOI
\doi{https://doi.org/10.1145/3313831.XXXXXXX}
% ISBN
\isbn{978-1-4503-6708-0/20/04}
%Conference
\conferenceinfo{CHI'20,}{April  25--30, 2020, Honolulu, HI, USA}
%Price
\acmPrice{\$15.00}

% Use this command to override the default ACM copyright statement
% (e.g. for preprints).  Consult the conference website for the
% camera-ready copyright statement.

%% HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP --
%% Please note you need to make sure the copy for your specific
%% license is used here!
% \toappear{
% Permission to make digital or hard copies of all or part of this work
% for personal or classroom use is granted without fee provided that
% copies are not made or distributed for profit or commercial advantage
% and that copies bear this notice and the full citation on the first
% page. Copyrights for components of this work owned by others than ACM
% must be honored. Abstracting with credit is permitted. To copy
% otherwise, or republish, to post on servers or to redistribute to
% lists, requires prior specific permission and/or a fee. Request
% permissions from \href{mailto:Permissions@acm.org}{Permissions@acm.org}. \\
% \emph{CHI '16},  May 07--12, 2016, San Jose, CA, USA \\
% ACM xxx-x-xxxx-xxxx-x/xx/xx\ldots \$15.00 \\
% DOI: \url{http://dx.doi.org/xx.xxxx/xxxxxxx.xxxxxxx}
% }

% Arabic page numbers for submission.  Remove this line to eliminate
% page numbers for the camera ready copy
% \pagenumbering{arabic}

% Load basic packages
\usepackage{balance}       % to better equalize the last page
\usepackage{graphics}      % for EPS, load graphicx instead 
\usepackage[T1]{fontenc}   % for umlauts and other diaeresis
\usepackage{txfonts}
\usepackage{mathptmx}
\usepackage[pdflang={en-US},pdftex]{hyperref}
\usepackage{color}
\usepackage{booktabs}
\usepackage{textcomp}

% Some optional stuff you might like/need.
\usepackage{microtype}        % Improved Tracking and Kerning
% \usepackage[all]{hypcap}    % Fixes bug in hyperref caption linking
\usepackage{ccicons}          % Cite your images correctly!
% \usepackage[utf8]{inputenc} % for a UTF8 editor only

% If you want to use todo notes, marginpars etc. during creation of
% your draft document, you have to enable the "chi_draft" option for
% the document class. To do this, change the very first line to:
% "\documentclass[chi_draft]{sigchi}". You can then place todo notes
% by using the "\todo{...}"  command. Make sure to disable the draft
% option again before submitting your final document.
\usepackage{todonotes}

% Paper metadata (use plain text, for PDF inclusion and later
% re-using, if desired).  Use \emtpyauthor when submitting for review
% so you remain anonymous.
\def\plaintitle{SIGCHI Conference Proceedings Format}
\def\plainauthor{First Author, Second Author, Third Author,
  Fourth Author, Fifth Author, Sixth Author}
\def\emptyauthor{}
\def\plainkeywords{Authors' choice; of terms; separated; by
  semicolons; include commas, within terms only; this section is required.}
\def\plaingeneralterms{Documentation, Standardization}

% llt: Define a global style for URLs, rather that the default one
\makeatletter
\def\url@leostyle{%
  \@ifundefined{selectfont}{
    \def\UrlFont{\sf}
  }{
    \def\UrlFont{\small\bf\ttfamily}
  }}
\makeatother
\urlstyle{leo}

% To make various LaTeX processors do the right thing with page size.
\def\pprw{8.5in}
\def\pprh{11in}
\special{papersize=\pprw,\pprh}
\setlength{\paperwidth}{\pprw}
\setlength{\paperheight}{\pprh}
\setlength{\pdfpagewidth}{\pprw}
\setlength{\pdfpageheight}{\pprh}

% Make sure hyperref comes last of your loaded packages, to give it a
% fighting chance of not being over-written, since its job is to
% redefine many LaTeX commands.
\definecolor{linkColor}{RGB}{6,125,233}
\hypersetup{%
  pdftitle={\plaintitle},
% Use \plainauthor for final version.
%  pdfauthor={\plainauthor},
  pdfauthor={\emptyauthor},
  pdfkeywords={\plainkeywords},
  pdfdisplaydoctitle=true, % For Accessibility
  bookmarksnumbered,
  pdfstartview={FitH},
  colorlinks,
  citecolor=black,
  filecolor=black,
  linkcolor=black,
  urlcolor=linkColor,
  breaklinks=true,
  hypertexnames=false
}

% create a shortcut to typeset table headings
% \newcommand\tabhead[1]{\small\textbf{#1}}

% End of preamble. Here it comes the document.
\begin{document}

\title{\plaintitle}

\numberofauthors{4}
\author{%
\alignauthor{Leave Authors Anonymous\\
    \affaddr{for Submission}\\
    \affaddr{City, Country}\\
    \email{e-mail address}}\\
\alignauthor{Leave Authors Anonymous\\
    \affaddr{for Submission}\\
    \affaddr{City, Country}\\
    \email{e-mail address}}\\
\alignauthor{Leave Authors Anonymous\\
    \affaddr{for Submission}\\
    \affaddr{City, Country}\\
    \email{e-mail address}}\\
\alignauthor{Leave Authors Anonymous\\
    \affaddr{for Submission}\\
    \affaddr{City, Country}\\
    \email{e-mail address}}\\
}

\maketitle

\begin{abstract}
  UPDATED---\today. This sample paper describes the formatting
  requirements for SIGCHI conference proceedings, and offers
  recommendations on writing for the worldwide SIGCHI
  readership. Please review this document even if you have submitted
  to SIGCHI conferences before, as some format details have changed
  relative to previous years. Abstracts should be about 150 words and
  are required.
\end{abstract}

% ACM Classfication

\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10003120.10003121</concept_id>
<concept_desc>Human-centered computing~Human computer interaction (HCI)</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003120.10003121.10003125.10011752</concept_id>
<concept_desc>Human-centered computing~Haptic devices</concept_desc>
<concept_significance>300</concept_significance>
</concept>
<concept>
<concept_id>10003120.10003121.10003122.10003334</concept_id>
<concept_desc>Human-centered computing~User studies</concept_desc>
<concept_significance>100</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Human-centered computing~Human computer interaction (HCI)}
\ccsdesc[300]{Human-centered computing~Haptic devices}
\ccsdesc[100]{Human-centered computing~User studies}

% Author Keywords
\keywords{\plainkeywords}

% Print the classficiation codes
\printccsdesc
Please use the 2012 Classifiers and see this link to embed them in the text: \url{https://dl.acm.org/ccs/ccs_flat.cfm}

\section{Introduction}

This format is to be used for submissions that are published in the
conference proceedings. We wish to give this volume a consistent,
high-quality appearance. We therefore ask that authors follow some
simple guidelines. You should format your paper exactly like this
document. The easiest way to do this is to replace the content with
your own material.  This document describes how to prepare your
submissions using \LaTeX.

\section{Page Size and Columns}
On each page your material should fit within a rectangle of 7 $\times$
9.15 inches (18 $\times$ 23.2 cm), centered on a US Letter page (8.5
$\times$ 11 inches), beginning 0.85 inches (1.9 cm) from the top of
the page, with a 0.3 inches (0.85 cm) space between two 3.35 inches
(8.4 cm) columns. Right margins should be justified, not
ragged. Please be sure your document and PDF are US letter and not A4.

\section{Typeset Text}
The styles contained in this document have been modified from the
default styles to reflect ACM formatting conventions. For example,
content paragraphs like this one are formatted using the Normal style.

\LaTeX\ sometimes will create overfull lines that extend into columns.
To attempt to combat this, the \texttt{.cls} file has a command,
\texttt{{\textbackslash}sloppy}, that essentially asks \LaTeX\ to
prefer underfull lines with extra whitespace.  For more details on
this, and info on how to control it more finely, check out
{\url{http://www.economics.utoronto.ca/osborne/latex/PMAKEUP.HTM}}.

\subsection{Title and Authors}

Your paper's title, authors and affiliations should run across the
full width of the page in a single column 17.8 cm (7 in.) wide.  The
title should be in Helvetica or Arial 18-point bold.  Authors' names
should be in Times New Roman or Times Roman 12-point bold, and
affiliations in 12-point regular.

See \texttt{{\textbackslash}author} section of this template for
instructions on how to format the authors. For more than three
authors, you may have to place some address information in a footnote,
or in a named section at the end of your paper. Names may optionally
be placed in a single centered row instead of at the top of each
column. Leave one 10-point line of white space below the last line of
affiliations.

\subsection{Abstract and Keywords}

Every submission should begin with an abstract of about 150 words,
followed by a set of Author Keywords and ACM Classification
Keywords. The abstract and keywords should be placed in the left
column of the first page under the left half of the title. The
abstract should be a concise statement of the problem, approach, and
conclusions of the work described. It should clearly state the paper's
contribution to the field of HCI\@.

\subsection{Normal or Body Text}

Please use a 10-point Times New Roman or Times Roman font or, if this
is unavailable, another proportional font with serifs, as close as
possible in appearance to Times Roman 10-point. Other than Helvetica
or Arial headings, please use sans-serif or non-proportional fonts
only for special purposes, such as source code text.

\subsection{First Page Copyright Notice}
This template include a sample ACM copyright notice at the bottom of
page 1, column 1.  Upon acceptance, you will be provided with the
appropriate copyright statement and unique DOI string for publication.
Accepted papers will be distributed in the conference
publications. They will also be placed in the ACM Digital Library,
where they will remain accessible to thousands of researchers and
practitioners worldwide. See
\url{http://acm.org/publications/policies/copyright_policy} for the
ACM's copyright and permissions policy.

\subsection{Subsequent Pages}

On pages beyond the first, start at the top of the page and continue
in double-column format.  The two columns on the last page should be
of equal length.

\begin{figure}
\centering
  \includegraphics[width=0.9\columnwidth]{figures/sigchi-logo}
  \caption{Insert a caption below each figure. Do not alter the
    Caption style.  One-line captions should be centered; multi-line
    should be justified. }~\label{fig:figure1}
\end{figure}

\subsection{References and Citations}

Use a numbered list of references at the end of the article, ordered
alphabetically by last name of first author, and referenced by numbers
in
brackets~\cite{acm_categories,ethics,Klemmer:2002:WSC:503376.503378}.
Your references should be published materials accessible to the
public. Internal technical reports may be cited only if they are
easily accessible (i.e., you provide the address for obtaining the
report within your citation) and may be obtained by any reader for a
nominal fee. Proprietary information may not be cited. Private
communications should be acknowledged in the main text, not referenced
(e.g., ``[Borriello, personal communication]'').

References should be in ACM citation format:
\url{http://acm.org/publications/submissions/latex_style}. This
includes citations to internet
resources~\cite{acm_categories,cavender:writing,CHINOSAUR:venue,psy:gangnam}
according to ACM format, although it is often appropriate to include
URLs directly in the text, as above.

% Use a numbered list of references at the end of the article, ordered
% alphabetically by first author, and referenced by numbers in
% brackets~\cite{ethics, Klemmer:2002:WSC:503376.503378,
%   Mather:2000:MUT, Zellweger:2001:FAO:504216.504224}. For papers from
% conference proceedings, include the title of the paper and an
% abbreviated name of the conference (e.g., for Interact 2003
% proceedings, use \textit{Proc. Interact 2003}). Do not include the
% location of the conference or the exact date; do include the page
% numbers if available. See the examples of citations at the end of this
% document. Within this template file, use the \texttt{References} style
% for the text of your citation.

% Your references should be published materials accessible to the
% public.  Internal technical reports may be cited only if they are
% easily accessible (i.e., you provide the address for obtaining the
% report within your citation) and may be obtained by any reader for a
% nominal fee.  Proprietary information may not be cited. Private
% communications should be acknowledged in the main text, not referenced
% (e.g., ``[Robertson, personal communication]'').

\begin{table}
  \centering
  \begin{tabular}{l r r r}
    % \toprule
    & & \multicolumn{2}{c}{\small{\textbf{Test Conditions}}} \\
    \cmidrule(r){3-4}
    {\small\textit{Name}}
    & {\small \textit{First}}
      & {\small \textit{Second}}
    & {\small \textit{Final}} \\
    \midrule
    Marsden & 223.0 & 44 & 432,321 \\
    Nass & 22.2 & 16 & 234,333 \\
    Borriello & 22.9 & 11 & 93,123 \\
    Karat & 34.9 & 2200 & 103,322 \\
    % \bottomrule
  \end{tabular}
  \caption{Table captions should be placed below the table. We
    recommend table lines be 1 point, 25\% black. Minimize use of
    table grid lines.}~\label{tab:table1}
\end{table}

\section{Sections}

The heading of a section should be in Helvetica or Arial 9-point bold,
all in capitals. Sections should \textit{not} be numbered.

\subsection{Subsections}

Headings of subsections should be in Helvetica or Arial 9-point bold
with initial letters capitalized.  For sub-sections and
sub-subsections, a word like \emph{the} or \emph{of} is not
capitalized unless it is the first word of the heading.

\subsubsection{Sub-subsections}

Headings for sub-subsections should be in Helvetica or Arial 9-point
italic with initial letters capitalized.  Standard
\texttt{{\textbackslash}section}, \texttt{{\textbackslash}subsection},
and \texttt{{\textbackslash}subsubsection} commands will work fine in
this template.

\section{Figures/Captions}

Place figures and tables at the top or bottom of the appropriate
column or columns, on the same page as the relevant text (see
Figure~\ref{fig:figure1}). A figure or table may extend across both
columns to a maximum width of 17.78 cm (7 in.).

\begin{figure*}
  \centering
  \includegraphics[width=1.75\columnwidth]{figures/map}
  \caption{In this image, the map maximizes use of space. You can make
    figures as wide as you need, up to a maximum of the full width of
    both columns. Note that \LaTeX\ tends to render large figures on a
    dedicated page. Image: \ccbynd~ayman on
    Flickr.}~\label{fig:figure2}
\end{figure*}

Captions should be Times New Roman or Times Roman 9-point bold.  They
should be numbered (e.g., ``Table~\ref{tab:table1}'' or
``Figure~\ref{fig:figure1}''), centered (if one line) otherwise justified, and placed beneath the figure
or table.  Please note that the words ``Figure'' and ``Table'' should
be spelled out (e.g., ``Figure'' rather than ``Fig.'') wherever they
occur. Figures, like Figure~\ref{fig:figure2}, may span columns and
all figures should also include alt text for improved accessibility.
Papers and notes may use color figures, which are included in the page
limit; the figures must be usable when printed in black-and-white in
the proceedings.

The paper may be accompanied by a short video figure (we recommend staying within five
minutes in length). However, the paper should stand on its own without
the video figure, as the video may not be available to everyone who
reads the paper.

\subsection{Inserting Images}
When possible, include a vector formatted graphic (i.e. PDF or EPS).
When including bitmaps,  use an image editing tool to resize the image
at the appropriate printing resolution (usually 300 dpi).

\section{Quotations}
Quotations may be italicized when \textit{``placed inline''}.

\begin{quote}
Longer quotes, when placed in their own paragraph, need not be
italicized or in quotation marks when indented.  
\end{quote}

\section{Language, Style, and Content}

The written and spoken language of SIGCHI is English. Spelling and
punctuation may use any dialect of English (e.g., British, Canadian,
US, etc.) provided this is done consis- tently. Hyphenation is
optional. To ensure suitability for an international audience, please
pay attention to the following:

\begin{itemize}
\item Write in a straightforward style.
\item Try to avoid long or complex sentence structures.
\item Use common and basic vocabulary (e.g., use the word ``unusual'' rather than the word ``arcane''.
\item Briefly define or explain all technical terms that may be
  unfamiliar to readers.
\item Explain all acronyms the first time they are used in your
  text---e.g., ``Digital Signal Processing (DSP)''.
\item Explain local references (e.g., not everyone knows all city
  names in a particular country).
\item Explain ``insider'' comments. Ensure that your whole audience
  understands any reference whose meaning you do not describe (e.g.,
  do not assume that everyone has used a Macintosh or a particular
  application).
\item Explain colloquial language and puns. Understanding phrases like
  ``red herring'' may require a local knowledge of English.  Humor and
  irony are difficult to translate.
\item Use unambiguous forms for culturally localized concepts, such as
  times, dates, currencies, and numbers (e.g., ``1--5--97'' or
  ``5/1/97'' may mean 5 January or 1 May, and ``seven o'clock'' may
  mean 7:00 am or 19:00). For currencies, indicate equivalences:
  ``Participants were paid {\fontfamily{txr}\selectfont \textwon}
  25,000, or roughly US \$22.''
\item Be careful with the use of gender-specific pronouns (he, she)
  and other gendered words (chairman, manpower, man-months). Use
  inclusive language that is gender-neutral (e.g., she or he, they,
  s/he, chair, staff, staff-hours, person-years). See the
  \textit{Guidelines for Bias-Free Writing} for further advice and
  examples regarding gender and other personal
  attributes~\cite{Schwartz:1995:GBF}. Be particularly aware of
  considerations around writing about people with disabilities.
\item If possible, use the full (extended) alphabetic character set
  for names of persons, institutions, and places (e.g.,
  Gr{\o}nb{\ae}k, Lafreni\'ere, S\'anchez, Nguy{\~{\^{e}}}n,
  Universit{\"a}t, Wei{\ss}enbach, Z{\"u}llighoven, \r{A}rhus, etc.).
  These characters are already included in most versions and variants
  of Times, Helvetica, and Arial fonts.
\end{itemize}

\section{Accessibility}
The Executive Council of SIGCHI has committed to making SIGCHI
conferences more inclusive for researchers, practitioners, and
educators with disabilities. As a part of this goal, the all authors
are asked to work on improving the accessibility of their
submissions. Specifically, we encourage authors to carry out the
following five steps:
\begin{enumerate}
\item Add alternative text to all figures
\item Mark table headings
\item Add tags to the PDF
\item Verify the default language
\item Set the tab order to ``Use Document Structure''
\end{enumerate}
For more information and links to instructions and resources, please
see: \url{http://chi2016.acm.org/accessibility}.  The
\texttt{{\textbackslash}hyperref} package allows you to create well tagged PDF files,
please see the preamble of this template for an example.

\section{Page Numbering, Headers and Footers}
Your final submission should not contain footer or header information
at the top or bottom of each page. Specifically, your final submission
should not include page numbers. Initial submissions may include page
numbers, but these must be removed for camera-ready. Page numbers will
be added to the PDF when the proceedings are assembled.

\section{Producing and Testing PDF Files}

We recommend that you produce a PDF version of your submission well
before the final deadline.  Your PDF file must be ACM DL
Compliant. The requirements for an ACM Compliant PDF are available at:
{\url{http://www.scomminc.com/pp/acmsig/ACM-DL-pdfs-requirements.htm}}.

Test your PDF file by viewing or printing it with the same software we
will use when we receive it, Adobe Acrobat Reader Version 10. This is
widely available at no cost. Note that most
reviewers will use a North American/European version of Acrobat
reader, so please check your PDF accordingly.

\section{Conclusion}

It is important that you write for the SIGCHI audience. Please read
previous years' proceedings to understand the writing style and
conventions that successful authors have used. It is particularly
important that you state clearly what you have done, not merely what
you plan to do, and explain how your work is different from previously
published work, i.e., the unique contribution that your work makes to
the field. Please consider what the reader will learn from your
submission, and how they will find your work useful. If you write with
these questions in mind, your work is more likely to be successful,
both in being accepted into the conference, and in influencing the
work of our field.

\section{Acknowledgments}

Sample text: We thank all the volunteers, and all publications support
and staff, who wrote and provided helpful comments on previous
versions of this document. Authors 1, 2, and 3 gratefully acknowledge
the grant from NSF (\#1234--2012--ABC). \textit{This whole paragraph is
  just an example.}

% Balancing columns in a ref list is a bit of a pain because you
% either use a hack like flushend or balance, or manually insert
% a column break.  http://www.tex.ac.uk/cgi-bin/texfaq2html?label=balance
% multicols doesn't work because we're already in two-column mode,
% and flushend isn't awesome, so I choose balance.  See this
% for more info: http://cs.brown.edu/system/software/latex/doc/balance.pdf
%
% Note that in a perfect world balance wants to be in the first
% column of the last page.
%
% If balance doesn't work for you, you can remove that and
% hard-code a column break into the bbl file right before you
% submit:
%
% http://stackoverflow.com/questions/2149854/how-to-manually-equalize-columns-
% in-an-ieee-paper-if-using-bibtex
%
% Or, just remove \balance and give up on balancing the last page.
%
\balance{}

\section{References Format}
Your references should be published materials accessible to the
public. Internal technical reports may be cited only if they are
easily accessible and may be obtained by any reader for a nominal
fee. Proprietary information may not be cited. Private communications
should be acknowledged in the main text, not referenced (e.g.,
[Golovchinsky, personal communication]). References must be the same
font size as other body text. References should be in alphabetical
order by last name of first author. Use a numbered list of references
at the end of the article, ordered alphabetically by last name of
first author, and referenced by numbers in brackets. For papers from
conference proceedings, include the title of the paper and the name of
the conference. Do not include the location of the conference or the
exact date; do include the page numbers if available.

References should be in ACM citation format:
\url{http://www.acm.org/publications/submissions/latex_style}.  This
includes citations to Internet
resources~\cite{CHINOSAUR:venue,cavender:writing,psy:gangnam}
according to ACM format, although it is often appropriate to include
URLs directly in the text, as above. Example reference formatting for
individual journal articles~\cite{ethics}, articles in conference
proceedings~\cite{Klemmer:2002:WSC:503376.503378},
books~\cite{Schwartz:1995:GBF}, theses~\cite{sutherland:sketchpad},
book chapters~\cite{winner:politics}, an entire journal
issue~\cite{kaye:puc},
websites~\cite{acm_categories,cavender:writing},
tweets~\cite{CHINOSAUR:venue}, patents~\cite{heilig:sensorama}, 
games~\cite{supermetroid:snes}, and
online videos~\cite{psy:gangnam} is given here.  See the examples of
citations at the end of this document and in the accompanying
\texttt{BibTeX} document. This formatting is a edited version of the
format automatically generated by the ACM Digital Library
(\url{http://dl.acm.org}) as ``ACM Ref.'' DOI and/or URL links are
optional but encouraged as are full first names. Note that the
Hyperlink style used throughout this document uses blue links;
however, URLs in the references section may optionally appear in
black.

% BALANCE COLUMNS
\balance{}

% REFERENCES FORMAT
% References must be the same font size as other body text.
\bibliographystyle{SIGCHI-Reference-Format}
\bibliography{sample}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2021-01-14 draft.tex
Worked on the Implications for design section

@@
 \def\emptyauthor{}
-\def\plainkeywords{distance learning; study environment; work environment; motivation; pandemic;}
+\def\plainkeywords{distance learning; student; home office; study environment; work environment; motivation; pandemic; health; }
 \def\plaingeneralterms{Documentation, Standardization}
@@
 \begin{document}
-
 \title{\plaintitle}
-
-\numberofauthors{3}
-\author{%
+\numberofauthors{4}
+\author{
   \alignauthor{Author One\\
@@
 }
-
 \maketitle
-
 \begin{abstract}
@@
 
-At the start of 2020, most countries around the world have had to impose strict restriction upon public spaces and institution in order to combat the eventual spread of Covid-19 within their populations\cite{fauci_lane_redfield_2020}.
+At the start of 2020, most countries around the world have had to impose strict restriction upon public spaces and institution in order to combat the eventual spread of Covid-19 within their populations.
 One measure imposed upon the educational systems was to forbid as much as possible lectures and other educational activities within their campuses as to avoid unnecessary and possible life-threatening contact between members of the institutions.
@@
 Students have suddenly found themselves studying full time from the comfort of their home, not needing to travel to the universities campuses anymore.
-During their own experiences as students within the Summer 2020 semester, the authors have notice certain trends within their own behaviour and that of fellow students related to the unpreparedness of their own home-study environment and the rising motivational issues, and so, decided to perform an inquiry under the course work for the User Research Methods PR at the Technical University of Vienna, in order to investigate if indeed there was a general unpreparedness across the student population for such a drastic move to distance learning, as well as, if there is such a notion as a \emph{perfect study environment}, and in the end, conclude with a small \emph{tips and tricks} handbook which other students might find helpful in order to increase their comfort and motivation for studying at home and eventually decrease the amount of stress cause by social isolation.\cite{hossain_mental_2020}
+During their own experiences as students within the Summer 2020 semester, the authors have notice certain trends within their own behaviour and that of fellow students related to the unpreparedness of their own home-study environment and the rising motivational issues, and so, decided to perform an inquiry under the course work for the User Research Methods PR at the Technical University of Vienna, in order to investigate if indeed there was a general unpreparedness across the student population for such a drastic move to distance learning, as well as, if there is such a notion as a \emph{perfect study environment}, and in the end, conclude with a small \emph{tips and tricks} handbook which other students might find helpful in order to increase their comfort and motivation for studying at home and eventually decrease the amount of stress cause by social isolation.\cite{fauci_lane_redfield_2020, hossain_mental_2020}
 
@@
 
-Here we should probably talk about the previous papers we read about distance learning, social isolation, education during other pandemics, as well as papers about the research methodologies
+Here we should probably talk about the previous papers we read about distance learning, social isolation, education during other pandemics, as well as papers about the research methodologies.
 
@@
 \subsubsection{Research Questions}
-Before starting the
 
-\subsubsection{Methodologies}
+\subsection{Methodologies}
 In order to perform their research as best as possible, the authors have decided on utilizing three separate methodologies in order to achieve a coherent approach and take into account as many aspects related towards \emph{study environments} as possible.
@@
 
-\subsection{Auto-ethnography}
+\subsubsection{Auto-ethnography}
 
@@
 The structure of the document has been agreed upon unanimously by the team as so to avoid any potential issues related to data privacy of the resulting documents from the auto-ethnographic research.
+
 After signing the consent form, each researcher has had to conduct an inner-inquiry upon his or hers experience that resulted from the drastic change towards full-time studying from home, as well as making a comparison between their study/work environment and study workload between their previous semester (e.g.
@@
 Summer 2020, Winter 2020/2021).
-Upon finishing there report about their own experience, each researcher had to take a picture of their current study environment/s (see Figure~\ref{fig:figure1} as an example) and attach it to the report.
+
+Upon finishing their report about their own experience, each researcher had to take a picture of their current study environment/s (see Figure~\ref{fig:figure1} as an example) and attach it to the report.
 Afterwards all reports where analysed by each researcher, and researcher-participant had to perform a presentation of their experience to all other researchers.
-Findings culminating in organizing the information from a constructionist approach using Miro\footnote{\url{https://miro.com/}} and extracting possible interview questions for their findings.
+Findings culminating in organizing the information using thematic analysis using Miro\footnote{\url{https://miro.com/}} and extracting possible interview questions for their findings.
 After having decided on the possible interview questions, sample semi-structured interview took place, having one of the researchers as a participant, and two others as interviewer and observer.
 Upon finishing the sample interview, the interview question had been filtered to only five central questions as so to provide a structure for the incoming participant interviews.
-
 \begin{figure}
@@
 
-\subsection{Semi-structured Interviews}
+\subsubsection{Semi-structured Interviews}
+The 5 interview questions
+Who were the participants (general information), where the interviews were taken, how we found the participants, age, academic status, consent management, tools, analysing the interview, miro idea board / extracting data THEMATIC ANALYSING
 
-\subsection{Photographic Ethnography}
+Some people did not know how the pandemic will evolve so they did not prepare for a long home learning situation, we asked them how the ideal setup will look like or if they know the next semesters  will be remotely what will they change.
+
+issues: Single interviewer, no observer., subjectivity issues due to the participants being friends
+
+\subsubsection{Photographic Ethnography}
+Using the photo analysis method, the researches wanted to discover the study setups of students engaged in distance learning.
+The method was chose to give a better overview of essential items used by students for improving the health and comfort during online studies, at home.
+The participants agreed on sending a photo of their environment before the semi-structured online interviews.
+Moreover, the researchers shared photos of their personal setups used for remote studies.
+Two consents were used in the research: one sent to the participants before the semi-structured online interview, and another, for the researchers themselves, before starting the auto-ethnography process.
+The processes of storing, analyzing, anonymizing and deletion of the participants and researchers photos were covered in the mentioned consents.
+
+As visual recording of the personal space …, not all the participants agreed to expose their working space.
+A number of X photos was collected in the photo analysis process.
+A visual difference between the state of the learning environment before and after switching to distance learning could not been made, as the photos received by the researchers were taken in the actual context of the pandemic.
+Only one participant sent photos of their old and their actual setup.
+One participant sent a photo of their current setup, and two photos of setups that could serve as inspiration for their ideal setup.
+All photos received by the participants were used in the analyze process.
+
+\begin{figure}
+\centering
+  \includegraphics[width=0.9\columnwidth]{figures/perfect-setup}
+  \caption{A sample photo from the Photographic Ethnography method given by one of the participants, it is the desired "perfect study environment''}~\label{fig:figure1}
+\end{figure}
 
@@
 
+We need to talk about the research question results here.
+
+Our findings from the interviews
+
+Our findings from the photos: Both participants and from the auto-ethnography
+
+The analyze of the photos received from the participants and from the researchers involved in the study, showed unique, personalized study environments,  with a commune focus on ergonomics, efficiency and aesthetics.
+The result showed that the position of the working desk is usually located close to a direct source of natural light.
+The importance of a natural source of light was mentioned by several participants during the semi-structured online interview process.
+Items such as: second screen, laptop, lamp, plants, notebooks were …
+
 \section{Discussion}
+
+Things to talk about: 
+1.Universities could open libraries or study spaces. Even increase the amount of space post-pandemic, as an issue already existed
+2. Items that are we recommend to use for study and the uni should give discounts to
+3.
+
+\subsection{Limitations}
 
@@
 
+It is worth noting that the research presented within this paper is not meant necessarily to provide the HCI community with a new form of interaction or a profoundly new methodological approach in how human-computer interaction can be studied, but it is meant to be seen more through the lens of \cite{dourish_implications_2006} where the significance of \emph{``Implications for design''} stems from observing human habits within a highly isolated scenario where most of the study and work interactions are perpetuated solely through technology.
+The authors desire is not to emphasize the need for bigger screens, or more comfortable chairs, but to show how much of our lives \emph{can} be replaced through software.
+
+\subsection{Office of the next pandemic}
+
+Given our interviews with the participants, no clear generalizing statement can be drawn on previous study setups possessed before the enactment of social distancing norms.
+But several have attributed a more aware understanding of the need to have such an environment within their homes.
+Noticing the likely-hood of our current situation to continue for at least one more semester, multiple participants had come to the conclusion and indeed already have plans of improving their study and work environments.
+Putting in question if a need in providing highly economical solutions in so as to reduce the overall cost of creating such a setup might be the next and most valuable step for the industry to take.
+
+\subsection{Replacement of social interaction}
+
+Multiple participants have expressed an inner desired to talk about their motivational issues while studying in this new environment.
+And to our amazement, different solutions in coping have been applied by each, from simple \emph{Zoom} study meetups, to arguably illegal (though depending on the country, might not be) face-to-face lecture viewings.
+Here the authors would like to express that a proper replacement of the in-class lecture experience, still does not exist and some participants have even emphasized a small regress due to the constant gap in interactivity that distance learning cannot overcome.
+
 \section{Conclusions and future work}
+
+1. A study on a more diverse group of students
+2. A more in-depth study about motivational aspects
+3. West country rich 
+4. Didn’t realize the length of the pandemic
+5. What could the regulations look like?
+6. Maybe (?) we have a OK demographic picture of the participants (students)
 

### 2021-01-15 draft.tex
Went through half of the discussion.

@@
 % option again before submitting your final document.
-\usepackage{todonotes}
+% \usepackage{todonotes}
 
@@
 \def\plaintitle{Lifestyle and study equipment changes during distance learning}
-\def\plainauthor{First Author, Second Author, Third Author,
-  Fourth Author, Fifth Author, Sixth Author}
-\def\emptyauthor{}
+\def\plainauthor{First Author, Second Author, Third Author, Fourth Author}
+\def\emptyauthor{First Author, Second Author, Third Author, Fourth Author}
 \def\plainkeywords{distance learning; student; home office; study environment; work environment; motivation; pandemic; health; }
@@
 \definecolor{linkColor}{RGB}{6,125,233}
-\hypersetup{%
+\hypersetup{
   pdftitle={\plaintitle},
@@
     \affaddr{}\\
-    \email{}}\\
+    \email{}
+    }\\
   \alignauthor{Author Two\\
@@
     \affaddr{}\\
-    \email{}}\\
+    \email{}
+    }\\
   \alignauthor{Author Three\\
@@
     \affaddr{}\\
-    \email{}}\\
+    \email{}
+    }\\
   \alignauthor{Author Four\\
@@
     \affaddr{}\\
-    \email{}}\\
+    \email{}
+    }
 }
 \maketitle
+
 \begin{abstract}
-Given the appearance of the new pathological risk incurred during the 2020 Covid-19 pandemic, most educational institutions, be them either lower or higher educational, have had to restrict their activity on-campus and promote a fully online pedagogical methodology in order to avoid the spread of the virus and protect the health of both students and teachers.
+Given the appearance of the new pathological risk incurred during the 2020 COVID-19 pandemic, most educational institutions, be them either lower or higher educational, have had to restrict their activity on-campus and promote a fully online pedagogical methodology in order to avoid the spread of the virus and protect the health of both students and teachers.
 By employing already existing software solutions to the likes of \emph{Zoom}, \emph{Microsoft Teams}, and other existing tools, courses have been completely moved within the realm of the internet to the best of the ability of each educational institution.
@@
 % ACM Classfication
-
 \begin{CCSXML}
@@
 
-At the start of 2020, most countries around the world have had to impose strict restriction upon public spaces and institution in order to combat the eventual spread of Covid-19 within their populations.
+At the start of 2020, most countries around the world have had to impose strict restriction upon public spaces and institution in order to combat the eventual spread of COVID-19 within their populations.
 One measure imposed upon the educational systems was to forbid as much as possible lectures and other educational activities within their campuses as to avoid unnecessary and possible life-threatening contact between members of the institutions.
@@
 
-\subsubsection{Research Questions}
+\subsection{Research Questions}
 
@@
 
-Before starting the auto-ethnography research, each researcher has been given an information sheet and consent form which had to be sign by the research-participant and one of the other researchers.
-The structure of the document has been agreed upon unanimously by the team as so to avoid any potential issues related to data privacy of the resulting documents from the auto-ethnographic research.
+Before starting the auto-ethnography research, each researcher has been given an information sheet and consent form which had to be sign by the research-participant\footnote{The researcher that takes to role as participant as well, within the methodology} and one of the other researchers.
+The structure of the document has been agreed upon unanimously by the team so as to avoid any potential issues related to data privacy of the resulting documents from the auto-ethnographic research.
 
-After signing the consent form, each researcher has had to conduct an inner-inquiry upon his or hers experience that resulted from the drastic change towards full-time studying from home, as well as making a comparison between their study/work environment and study workload between their previous semester (e.g.
-Winter 2019/2020) and the next restricted semesters (e.g.
-Summer 2020, Winter 2020/2021).
+After signing the consent form, each researcher has had to conduct an inner-inquiry upon his or hers experience that resulted from the drastic change towards full-time studying from home, as well as making a comparison between their study/work environment and study workload between their previous semester\footnote{Winter 2019/2020} and the next restricted semesters\footnote{Summer 2020 and Winter 2020/2021}.
 
-Upon finishing their report about their own experience, each researcher had to take a picture of their current study environment/s (see Figure~\ref{fig:figure1} as an example) and attach it to the report.
-Afterwards all reports where analysed by each researcher, and researcher-participant had to perform a presentation of their experience to all other researchers.
-Findings culminating in organizing the information using thematic analysis using Miro\footnote{\url{https://miro.com/}} and extracting possible interview questions for their findings.
-After having decided on the possible interview questions, sample semi-structured interview took place, having one of the researchers as a participant, and two others as interviewer and observer.
-Upon finishing the sample interview, the interview question had been filtered to only five central questions as so to provide a structure for the incoming participant interviews.
+Upon finishing their report about their own experience, each researcher had to take a picture of their current study environment (see Figure~\ref{fig:figure1} as an example) and attach it to the report.
+Afterwards all reports where analysed by each researcher and the  researcher-participant had to perform a presentation of their experience to all other researchers.
+Later on, the information was analysed using \emph{thematic analysis} within \emph{Miro}\footnote{\url{https://miro.com/}} so as to extract possible interview questions for later use.
+After having decided on the possible interview questions, a sample semi-structured interview took place, having one of the researchers as a participant, and two others as interviewer and observer.
+Upon finishing the sample interview, the interview questions had been filtered to only five central ones in order to be used as a guide for the incoming participant interviews.
 \begin{figure}
 \centering
-  \includegraphics[width=0.9\columnwidth]{figures/auto-e-picture}
+  \includegraphics[width=1\columnwidth]{figures/auto-e-picture}
   \caption{Sample picture from the Auto-Ethnographic method, showing the desk of one of the researchers}~\label{fig:figure1}
@@
 The 5 interview questions
-Who were the participants (general information), where the interviews were taken, how we found the participants, age, academic status, consent management, tools, analysing the interview, miro idea board / extracting data THEMATIC ANALYSING
+Who were the participants (general information), where the interviews were taken, how we found the participants, age, academic status, consent management, tools, analysing the interview, Miro idea board / extracting data THEMATIC ANALYSING
 
@@
 Using the photo analysis method, the researches wanted to discover the study setups of students engaged in distance learning.
-The method was chose to give a better overview of essential items used by students for improving the health and comfort during online studies, at home.
+The method was chosen in order to give a better overview of essential items used by students for improving their health and comfort during online studies, at home.
 The participants agreed on sending a photo of their environment before the semi-structured online interviews.
@@
 
-As visual recording of the personal space …, not all the participants agreed to expose their working space.
-A number of X photos was collected in the photo analysis process.
+As visual recording of the personal space can be consider as a breach of privacy, not all the participants agreed to expose their working space.
+A number of five + (how many Oscar got) photos was collected in the photo analysis process.
 A visual difference between the state of the learning environment before and after switching to distance learning could not been made, as the photos received by the researchers were taken in the actual context of the pandemic.
 Only one participant sent photos of their old and their actual setup.
-One participant sent a photo of their current setup, and two photos of setups that could serve as inspiration for their ideal setup.
+One participant sent a photo of their current setup, and two photos of setups that could serve as inspiration for their ideal setup (see Figure~\ref{fig:figure2}).
 All photos received by the participants were used in the analyze process.
@@
 \centering
-  \includegraphics[width=0.9\columnwidth]{figures/perfect-setup}
-  \caption{A sample photo from the Photographic Ethnography method given by one of the participants, it is the desired "perfect study environment''}~\label{fig:figure1}
+  \includegraphics[width=1\columnwidth]{figures/perfect-setup}
+  \caption{A sample photo from the Photographic Ethnography method given by one of the participants, it is the desired "perfect study environment''}~\label{fig:figure2}
 \end{figure}
@@
 3.
+
+\subsection{Biases in participation}
+There was an obvious variation in the result we achieved.
+It is therefore feasible to discuss what the research results would have looked like if the number of participants had been higher, or if the participants had studied another educational discipline than engineering.
+All the participants were students at the Vienna University of Technology in Austria which is a delimitation.
+Anyway, we believe it was an decent variety of life situations among these participants and thus a representative research overview.
+
+To try to minimize biases in the thematic analysis, all of the participants were renamed to improve an transparent thematic coding.
+
+However, we argue that unaware biases could still affect the participants behavior and our own interpretations because we knew these students before the research.
+
+\subsection{Motivation}
+But regardless of the participants' background a trend of declining motivation emerged in the research, something we did not plan for.
+All participants referred several times during the interviews to arguments that they experienced a deteriorating level of motivation despite the fact that we did not ask any semi-structured question about motivation.
+Motivation can therefore be seen as a rising and hidden problem even if the student's home office equipment or home office studies worked out well.
+We want to attribute the deteriorating motivation to the prevailing pandemic that forces students to study from home and be isolated from the campus life.
+What the challenges could entail varied depending on the participants.
+Two participants clearly stated that they did not appreciate studying without their classmates.
+One student was missing the sunlight and feeling of freedom.
+Another student found it difficult to focus on the computer screen during eight hours, but had no big challenges studying remotely.
+We also saw a pattern that the participants' motivation was stronger in the first semester of the pandemic (2020S) compared with the second semester of the pandemic (2020W).
+
+We believe this can be addressed to the society’s first ignorance of the early pandemic and that people primarily thought the early virus situation would not last for long.
+We therefore claim that the students' motivation was slightly better during the first semester because they kept their spirits up.
+This allowed the students to complete their studies in a distance learning format during the first semester of the pandemic without being too negatively affected.
+
+\subsection{Equipment}
+This can also be seen as an argument as to why six out of eight participants acquired new technical equipment in the middle of the pandemic, when it was clearer distance learning would continue.
+Upgrading the home office was eventually considered a necessity now when the students realized that their home office would remain.
+The technical equipment that was most commonly bought among the participants were extra monitors, touchpads, printers, headphones and mouses.
+However, we argue that it is still difficult to generalize what type of technical equipment students need to add in their home office setup due to the fact that the setup differs from situations.
+It can be stated that none of the participants needed to buy a computer to be able to transform into the distance learning format.
+We believe that this is due to the fact that the university and university studies were already digitized to a large extent before the pandemic broke out.
+Consequently, as a student switching to full-distance learning was not too painful even though the motivation has been strongly negatively affected.
+As the technical equipment is central to distance learning, we believe that students in general have chosen to prioritize a decent set-up.
+We believe that many students prioritize buying the most relevant technical equipment at the beginning of their university education.
+However, we believe that most students have needed to update some of the technical equipment.
+Only one of nine participants had for example not bought any extra electrical equipment in 2020.
+A short conclusion is therefore that most home offices were not optimized for distance learning at the beginning of the pandemic and that many students have had to upgrade their equipment successively.
+
+\subsection{Ergonomics and comfort}
+Studying in the home office sets a new level of understanding ergonomics depending on the basic office equipment.
+We would like to point out that there was dissatisfaction with the participants' office chairs, which they considered to be unergonomic in many various aspects.
+The chair was described as stiff, offered a bad working posture and could not be adjusted in height.
+Hence, it was not an office chair but a normal chair.
+We therefore claim that there may be negative effects in the back, neck and shoulder if students do not choose to upgrade their chair in the future home office.
+Studying at the university offers better ergonomics with chairs, benches and lamps that are adapted for university studies.
+Consequently, five of the participants answered that they wanted to upgrade their chair if they could.
+Three of the participants also answered that they would prefer to have a separate office if they could, which is not possible without moving into a new living accommodation.
+We therefore believe that it is necessary for all students to reflect our their own situation and be flexible and creative in how they can improve their own home office.
+All students may need different solutions as situations always differ.
+We also believe that inappropriate routines that office equipment can generate are difficult to detect.
+It is easy to get used to equipment that works but is not optimal.
+We therefore urge all students to reflect about their home office standard and how it could be improved.
+We consider it is important to ask the question "what do I need to improve if I am going to study here for a year?".
+According to the research findings, all participants received some form of negative ergonomics aspect that affected the participants’ studies.
+Working light, fresh air or working posture were the some main problems.
+Even sitting still in one and the same room was considered as a problem.
+Improving the study area as early as possible, we claim will prevent discovered and undiscovered problems.
+We base this discussion on the fact that the participants had difficulty answering questions about their perfect study setup.
+We thus argue that the participants had not processed their own thoughts about whether they could improve their home office or not, which indicates that ergonomics have been prioritized away in the noise of distance studies and other undiscovered problems.
+This can, for example, be related to the general student's financial limitations.
+One of the participants also pointed out that his eyes ached in the evening, after hours in front of the computer.
+But this can be avoided with regular breaks or blue light-repellent glasses, which is also an indication that the student does not know how to improve their ergonomics.
+We believe that this is not because the student does not want to improve his health, but because the student don not prioritize the time of reflecting about the home office setup.
+We would therefore like to encourage all higher education institutions as well as students to investigate the research that today exists on how to improve ergonomics in the home office.
 
@@
 5. What could the regulations look like?
-6. Maybe (?) we have a OK demographic picture of the participants (students)
+6. Maybe (?) we have a OK demographic picture of the participants (students) \\
 

### 2021-01-16 draft.tex
Changes on "Discussion" - Dragos

@@
 \centering
-  \includegraphics[width=1\columnwidth]{figures/auto-e-picture}
+  \includegraphics[width=1\columnwidth]{figures/auto-ethnography.JPG}
   \caption{Sample picture from the Auto-Ethnographic method, showing the desk of one of the researchers}~\label{fig:figure1}
+\end{figure}
+
+\begin{figure}
+\centering
+  \includegraphics[width=1\columnwidth]{figures/auto-ethnography-annotated.JPG}
+  \caption{The same sample picture from the Auto-Ethnographic method, now annotated with small comments from Miro}~\label{fig:figure2}
 \end{figure}
@@
   \includegraphics[width=1\columnwidth]{figures/perfect-setup}
-  \caption{A sample photo from the Photographic Ethnography method given by one of the participants, it is the desired "perfect study environment''}~\label{fig:figure2}
+  \caption{A sample photo from the Photographic Ethnography method given by one of the participants, it is the desired "perfect study environment''}~\label{fig:figure3}
 \end{figure}
@@
 The analyze of the photos received from the participants and from the researchers involved in the study, showed unique, personalized study environments,  with a commune focus on ergonomics, efficiency and aesthetics.
+For a better understanding of the students environment, the photo sent by the participants were used as a complementary visualization for the description given in the semi-structured interviews.
 The result showed that the position of the working desk is usually located close to a direct source of natural light.
 The importance of a natural source of light was mentioned by several participants during the semi-structured online interview process.
-Items such as: second screen, laptop, lamp, plants, notebooks were …
+Items such as: second screen, laptop, lamp, plants, notebooks were founded present in most of the study setups.
+The participants explained that the use of a second screen can improve productivity as you can easily multitask when required.
+When asked about an improvement they would made to the actual setup, participants that were not possessing any additional display mentioned the benefits they would get from owning one.
 
 \section{Discussion}
-
-Things to talk about: 
-1.Universities could open libraries or study spaces. Even increase the amount of space post-pandemic, as an issue already existed
-2. Items that are we recommend to use for study and the uni should give discounts to
-3.
 
@@
 Anyway, we believe it was an decent variety of life situations among these participants and thus a representative research overview.
+Upon a closer look within the participant’s characteristic, it must be noted that our “sample” is not very diverse from a geographical point of view.
+All participants, including the researchers themselves live and study either in Austria or another EU member country.
+In terms of degree, only Bachelors, Masters and PhD students have participated, no lower education.
+The degree’s have been mostly IT related and both from TU Wien and other European universities as well as Erasmus students
 
@@
 However, we argue that unaware biases could still affect the participants behavior and our own interpretations because we knew these students before the research.
+A very important bias that had occurred within our interviews is due to the already existing relationships between the researchers and the interview participants as well as the decision of not utilizing the classical interviewer/observer technique due to time constraints as well as the avoidance of causing discomfort towards the participants due to talking about their lives with an unknown person in the interview.
 
@@
 
-\subsection{Ergonomics and comfort}
+\subsection{Health and comfort}
 Studying in the home office sets a new level of understanding ergonomics depending on the basic office equipment.
-We would like to point out that there was dissatisfaction with the participants' office chairs, which they considered to be unergonomic in many various aspects.
-The chair was described as stiff, offered a bad working posture and could not be adjusted in height.
-Hence, it was not an office chair but a normal chair.
-We therefore claim that there may be negative effects in the back, neck and shoulder if students do not choose to upgrade their chair in the future home office.
+We would like to point out that there was dissatisfaction with the participants' office chairs, which most have described as being "unergonomic''.
+The chairs were described as stiff, offered a bad working posture and could not be adjusted in height.
+We therefore claim that there might be persistent health issues if students do not choose to upgrade their chair in the future home office.
 Studying at the university offers better ergonomics with chairs, benches and lamps that are adapted for university studies.
@@
 Three of the participants also answered that they would prefer to have a separate office if they could, which is not possible without moving into a new living accommodation.
-We therefore believe that it is necessary for all students to reflect our their own situation and be flexible and creative in how they can improve their own home office.
+We therefore believe that it is necessary for all students to reflect on their own situation and be flexible and creative in how they can improve their own home office.
 All students may need different solutions as situations always differ.
@@
 We therefore urge all students to reflect about their home office standard and how it could be improved.
-We consider it is important to ask the question "what do I need to improve if I am going to study here for a year?".
-According to the research findings, all participants received some form of negative ergonomics aspect that affected the participants’ studies.
-Working light, fresh air or working posture were the some main problems.
-Even sitting still in one and the same room was considered as a problem.
-Improving the study area as early as possible, we claim will prevent discovered and undiscovered problems.
-We base this discussion on the fact that the participants had difficulty answering questions about their perfect study setup.
-We thus argue that the participants had not processed their own thoughts about whether they could improve their home office or not, which indicates that ergonomics have been prioritized away in the noise of distance studies and other undiscovered problems.
-This can, for example, be related to the general student's financial limitations.
+We consider it important to ask the question "what do I need to improve if I am going to study here for a year?".
+According to the research findings, all participants received some form of negative ergonomics aspect that affected their studies.
+Good lighting, fresh air or working posture have been the main problems detected.
+Sitting still in one and the same room was considered as a negative aspect of distance learning.
+Improving the study area as early as possible, we claim will prevent easy to avoid health issues in the long run.
+
 One of the participants also pointed out that his eyes ached in the evening, after hours in front of the computer.
-But this can be avoided with regular breaks or blue light-repellent glasses, which is also an indication that the student does not know how to improve their ergonomics.
-We believe that this is not because the student does not want to improve his health, but because the student don not prioritize the time of reflecting about the home office setup.
-We would therefore like to encourage all higher education institutions as well as students to investigate the research that today exists on how to improve ergonomics in the home office.
+But this can be avoided with regular breaks or blue light-repellent glasses, a solution that the participant did not think about.
+We believe that this is not because the student does not want to improve his health, but because the student does not prioritize the time of reflecting about the home office setup.
+We would therefore like to encourage all higher education institutions to offer students a sort of \emph{tips and tricks manual} based on existing research on ergonomics and other desk related comfort improvements in order to better prepare students towards distance learning and gather their attention on the matter.
 
-\subsection{Limitations}
+\subsection{Financial Limitations}
+From the fact that participants had difficulty answering questions about their perfect study setup, we argue that they had not processed their own thoughts about whether they could improve their home office or not, which indicates that ergonomics have been prioritized away in the hectic noise of distance learning as well financial limitations.
+While most of our participants also work, several do not, and one has actually had their job activity interrupted due to the ongoing pandemic restrictions.
+And so financial limitations have halted their desire of improving their work environment further.
+Possible partnerships between educational institutions and retailers in order to provide discounts for students could prove effective in cutting costs on behalf of the students and even boost sales for retails, providing a win-win solution.
+Another solution could be found from the already established furniture rental services, that currently work with other companies in facilitating their move within cities like Vienna, by starting to provide also low to mid end study equipment for Erasmus students.
 
@@
 Thank you to all our interview participants for taking their time off their studies and work in order to help us with this assignment.
-Thank you to TU Wien for giving us access to the needed tools in order to prepare the assignment,  \textit{as good as they are}.
-No other funding was provided.
+Thank you to TU Wien for giving us access to the needed tools in order to prepare the assignment, and of course to our supervisory professors for offering us guidance along the way.
 

### 2021-01-31 Appendix.tex
Finished the paper

% Load basic packages
\usepackage{balance}       % to better equalize the last page
\usepackage{graphics}      % for EPS, load graphicx instead 
\usepackage[T1]{fontenc}   % for umlauts and other diaeresis
\usepackage{txfonts}
\usepackage{mathptmx}
\usepackage[pdflang={en-US},pdftex]{hyperref}
\usepackage{color}
\usepackage{booktabs}
\usepackage{textcomp}
\usepackage{lipsum}

\usepackage{comment} %OSCARs insert

\section{Appendix 1}

\subsection{Statement of team roles/contributions}

All team members conducted auto-ethnography, online semi-structured interviews, and photography ethnography, as well in transcribing and analyzing the collected data in Temi and Miro. We all remained in constant contact throughout the project, and each contributed valuable and creative input. The conference paper is written by the team together. However, the headlines have had main authors and secondary authors. Below you will find a brief overview of the individuals' roles and areas of responsibility.

\subsection{Andreea Roman}

Contributed with the preparation of the Industry Presentation, the creation of the leaflet included in it (with the illustrations from the designer). Worked on Findings of Auto-ethnography, Photo ethnography, Conclusion and Future work. Helped with Miro organization.

\subsection{Dragos-Alexandru Gabor}

Contributed by creating the consent forms and information sheets. Coordinated the e-signing effort between researchers and participants. Helped organize the Miro board before meetings. Set up the LaTeX report. Within the final report, worked mainly on Abstract, Introduction, Related work, Auto-ethnography, Implications for design.

\subsection{Joanna Zamiechowska}

Worked mainly on the Interview Methodologies and Findings section, partly in Discussions, Implications for Design, and Conclusions and Future Work, with secondary contributions in other sections throughout the paper. Researched semi-structured interview methodology. Researched literature and contributed literature in the references. Chief editor and proofreader, with contribution from the other teammates in this effort.

\subsection{Oscar Larsson}

Team coordinator, logistics coordinator, and contact person for the university. Responsible for submitting work assignments in TUWEL. Set up the “MS Teams platform” which has been our main information arena in the research project. Here we have structured and analyzed our data, as well as reviewed our internal documents and deadlines. Main author of the headings Introduction, RQ, Discussion, and Conclusion and Future Work. Secondary author of the headlines Abstract and Related Works. Prepared the first draft of both class presentations. I have also worked a lot with grammar and formalities in the various sub-reports, especially in LaTeX.

\subsection{General statement} 
Everyone worked on everything. Everyone. Best team ever!

### 2021-01-31 draft.tex
Finished the paper

--- 2021-01-14 draft.tex
@@
 %Price
-%\acmPrice{\$15.00}
+%\acmPrice{\$99.90}
 
@@
 % page numbers for the camera ready copy
-% \pagenumbering{arabic}
+\pagenumbering{arabic}
 
@@
 
+\usepackage{comment} %OSCARs insert
+
 % Some optional stuff you might like/need.
@@
 % so you remain anonymous.
-\def\plaintitle{Lifestyle and study equipment changes during distance learning}
-\def\plainauthor{First Author, Second Author, Third Author,
-  Fourth Author, Fifth Author, Sixth Author}
-\def\emptyauthor{}
-\def\plainkeywords{distance learning; student; home office; study environment; work environment; motivation; pandemic; health; }
+\def\plaintitle{The Pandemic Home Office For University Studies}
+\def\plainauthor{First Author, Second Author, Third Author, Fourth Author}
+\def\emptyauthor{First Author, Second Author, Third Author, Fourth Author}
+\def\plainkeywords{distance learning; health; home office; motivation; pandemic; student;  study environment; work environment;}
 \def\plaingeneralterms{Documentation, Standardization}
@@
 \numberofauthors{4}
+
 \author{
-  \alignauthor{Author One\\
-    \affaddr{for Submission}\\
-    \affaddr{}\\
-    \email{}}\\
-  \alignauthor{Author Two\\
-    \affaddr{for Submission}\\
-    \affaddr{}\\
-    \email{}}\\
-  \alignauthor{Author Three\\
-    \affaddr{for Submission}\\
-    \affaddr{}\\
-    \email{}}\\
-  \alignauthor{Author Four\\
-    \affaddr{for Submission}\\
-    \affaddr{}\\
-    \email{}}\\
+    Andreea-Valentina Roman\\
+    \affaddr{Vienna University of Technology}\\
+    \affaddr{Vienna, Austria}\\
+    \email{e12019805@student.tuwien.ac.at}
+    \and
+  Dragos-Alexandru Gabor\\
+    \affaddr{Vienna University of Technology}\\
+    \affaddr{Vienna, Austria}\\
+    \email{e11932446@student.tuwien.ac.at
 }
+ \and
+Joanna Zamiechowska\\
+    \affaddr{Vienna University of Technology}\\
+    \affaddr{Vienna, Austria}\\
+    \email{e11936038@student.tuwien.ac.at}
+ \and
+Oscar Larsson\\
+    \affaddr{Vienna University of Technology}\\
+    \affaddr{Vienna, Austria}\\
+    \email{e12015240@student.tuwien.ac.at}
+
+}
+
+\begin{comment}
+\author{
+  Andreea Roman\\
+  \affaddr{Vienna University of Technology}\\
+    \affaddr{Vienna, Austria}\\
+    \email{e12019805@student.tuwien.ac.at}
+  \and
+  Dragos-Alexandru Gabor\\
+  \affaddr{Vienna University of Technology}\\
+    \affaddr{Vienna, Austria}\\
+    \email{e12019805@student.tuwien.ac.at}
+    \AND
+  Dragos-Alexandru Gabor\\
+  \affaddr{Vienna University of Technology}\\
+    \affaddr{Vienna, Austria}\\
+    \email{e12019805@student.tuwien.ac.at}
+    \and
+  Dragos-Alexandru Gabor\\
+  \affaddr{Vienna University of Technology}\\
+    \affaddr{Vienna, Austria}\\
+    \email{e12019805@student.tuwien.ac.at}
+}
+\end{comment}
+
 \maketitle
+
 \begin{abstract}
-Given the appearance of the new pathological risk incurred during the 2020 Covid-19 pandemic, most educational institutions, be them either lower or higher educational, have had to restrict their activity on-campus and promote a fully online pedagogical methodology in order to avoid the spread of the virus and protect the health of both students and teachers.
-By employing already existing software solutions to the likes of \emph{Zoom}, \emph{Microsoft Teams}, and other existing tools, courses have been completely moved within the realm of the internet to the best of the ability of each educational institution.
-In this context, the authors are trying to investigate the effects that the sudden move to distance learning has had on students from different backgrounds, as well as how they have been forced to change their study and work environment to cope with the perpetual stress of academic life within the confines of their own home.
+Given the appearance of the new pathological risk incurred during the COVID-19 pandemic, most educational institutions, be they either lower or higher education, have had to restrict their on-campus activities and promote a fully online pedagogical approach in order to avoid the spread of the virus and protect the health of both students and teachers.
+By employing already existing software solutions facilitating video streaming (e.g.
+Zoom) and course management (e.g.
+Moodle), courses have, in most cases, been completely moved into the realm of the internet to the best of the ability of each educational institution.
+In this context, we are trying to investigate the effects that the sudden move to distance learning has had on students of different backgrounds, as well as how they have been forced to change their study and work environments to cope with the perpetual stress of academic life within the confines of their own home.
+After analyzing eight different student situations, there are indications that many students have a lower level of motivation in the current distance learning format.
+The technical equipment is upgraded but not always fully complete.
+There is still a majority who are not satisfied with their home office furnishings, mainly the office chair.
+However, there seems to be a lack of awareness of how simple ergonomics can be improved, partly because the student has downgraded this priority in the hope of soon returning to normal campus studies.
+Financial limitations are also a constraint.
 \end{abstract}
 
+%Not to use, repetitive: The equipment varies depending on the student and situation.
+
 % ACM Classfication
-
 \begin{CCSXML}
@@
 
-At the start of 2020, most countries around the world have had to impose strict restriction upon public spaces and institution in order to combat the eventual spread of Covid-19 within their populations.
-One measure imposed upon the educational systems was to forbid as much as possible lectures and other educational activities within their campuses as to avoid unnecessary and possible life-threatening contact between members of the institutions.
-In order to continue with the already started semester, most if not all education institutions have put forward online procedures based on already existing infrastructure in order for courses to still take place.
-Students have suddenly found themselves studying full time from the comfort of their home, not needing to travel to the universities campuses anymore.
-During their own experiences as students within the Summer 2020 semester, the authors have notice certain trends within their own behaviour and that of fellow students related to the unpreparedness of their own home-study environment and the rising motivational issues, and so, decided to perform an inquiry under the course work for the User Research Methods PR at the Technical University of Vienna, in order to investigate if indeed there was a general unpreparedness across the student population for such a drastic move to distance learning, as well as, if there is such a notion as a \emph{perfect study environment}, and in the end, conclude with a small \emph{tips and tricks} handbook which other students might find helpful in order to increase their comfort and motivation for studying at home and eventually decrease the amount of stress cause by social isolation.\cite{fauci_lane_redfield_2020, hossain_mental_2020}
+At the start of 2020, most countries around the world have had to impose strict restrictions upon public spaces and institutions in order to combat the eventual spread of COVID-19 within their population.
+One measure imposed upon the educational system was to forbid as much as possible lectures and other educational activities within their campuses as to avoid unnecessary and possibly life-threatening contact between students and members of the institution.
+In order to continue with the already started semester, most if not all education institutions have put forward online procedures based on existing infrastructure in order for the courses to still take place.
+Consequently, students have suddenly found themselves studying full-time from their homes, no longer allowed to study in libraries, cafes, or at the university campus.
+\\
+
+Not being able to study on campus as a student can be frustrating as well as challenging.
+A study from 2002 showed that "e-learning" was so challenging that approximately 80\% of those who participated in such a course would fail \cite{1}.
+Today, almost 20 years later, the circumstances have changed.
+Over the past 20 years, technology has developed radically and have improved conditions for how distance-based studies can be conducted.
+Since the turn of the millennium higher education institutions have had the opportunity to expand large parts of their functions with digital solutions \cite{2}.
+Offering distance learning not only improves students' study conditions but also allows better opportunities for the university to remain international, future-oriented, and profit-driven \cite{2}.
+For example, a university that offers distance learning attracts more students from other locations, nationally as well as internationally.
+Digital solutions in terms of online procedures and digital learning platforms are fundamental to the university's modern infrastructure, although this internal infrastructure has not previously been tested for a complete shift to distance learning during a pandemic.
+\\
+
+We, the research team of this conference paper, have also noticed certain trends of our own study behaviour during the distance learning semesters in Summer 2020 and Winter 2020.
+We have become aware of rising motivational issues due to distance learning.
+However, there is still an uncertainty as to whether this is true for the majority of the student population, and how unique situations may affect home learning.
+Hence, the following conference paper will perform an inquiry under a practice research study for the course \textit{193.056 User Research Methods Project} at Vienna University of Technology, Austria, in order to investigate this issue.
+The research study will examine if there is a general unpreparedness across the student population for such a drastic move to distance learning, as well as if there is such a notion as a \emph{``perfect study environment or study setup''}.
+This research result will help us compile recommendations for both students and educational institutions, which aim to help reduce the amount of stress caused by social isolation and full-time distance learning, and increase students' acceptance of the distance learning situation \cite{fauci_lane_redfield_2020, hossain_mental_2020}.
+
+%HCI, do we need more of this in this paper?
 
@@
 
-Here we should probably talk about the previous papers we read about distance learning, social isolation, education during other pandemics, as well as papers about the research methodologies.
+The following paper is related to a British motivation research study that examined the basic factors that influence successful distance learning \cite{simons_leverett_beaumont_2019}.
+The research established how the students' knowledge and autonomy relate to the inherent motivation in a distance-adapted study environment, and how the educational institution may affects this result.
+It should be added that this research was conducted before the COVID-19 pandemic and therefore describes a distance learning situation that differs from the current situation.
+However, the research identifies various factors that affect the students' results in a distance learning setting.
+We believe that continuously supporting the student is a fundamental factor for a successful outcome.
+This applies not only for universities but also for family, friends, and employers.
+Feedback needs to be adapted to each student.
+Communication should take place with one-to-one contact.
+Supporting the student means that the student is more likely to make conscious choices in their studies.
+Another important aspect is flexibility and the need to be able to adapt the studies depending on the students' needs.
+For example, accessing study materials online can be a form of flexibility.
+Consequently, intrinsic motivation consists of an interplay between support and flexibility, which should be taken into account when investigating this topic.
+
+Preceding all research methodologies, we conducted other literature reviews related to distance learning, home office studies, social isolation, and previous HCI related papers connected with the overall theme of the research questions and the methodologies used in our research.
+Four papers have been identified as either approaching the notion of distance learning motivation and competencies \cite{kolodziejczak_roszak_2017, simons_leverett_beaumont_2019}, students' preferred learning environments \cite{beckers_voordt_dewulf_2016}, or other works related to the impact that office comfort has on productivity \cite{sakellaris_et_al._2016}.
+
+Using \emph{Google Scholar} and the search inputs containing \emph{distance learning}, \emph{pandemic}, \emph{study environment}, \emph{COVID-19}, close to none have been found on the specific topic of the 2020 pandemic influences on distance learning, likely due to it being the first ever moment in human history that an epidemiological issue of this proportion has been encountered in the age of the internet, allowing the possibility of partaking in educational activities without putting one's life at risk.
+In the most relevant paper found, Lovric et al\cite{Lovri__2020}, the researchers performed an analysis on nursing students' perception of their overall experiences while studying during the COVID-19 pandemic, highlighting students' increasing worries and preference that educational institutions extend the already ongoing distance learning procedures.
+
+Upon reviewing different research methodologies and scientific papers through the course \emph{193.055 User Research Methods}, the authors have decided to proceed with a research strategy involving auto-ethnography, semi-structured interviews, and photographic ethnography\cite{adams_ellis_jones_2017, adams_2015, douglas_2003, schwartz_visual_1989} considering these methodologies as being the most appropriate, and capable of creating a coherent strategy for the short amount of time and resources available.
 
@@
 
-\subsubsection{Research Questions}
+The following section will describe the research question, as well as the methods used in the research study, to show how these methods are integrated with each other in order to create a research strategy.
+
+\subsection{Research Questions}
+
+A distinct but primitive research question was designed to guide the research.
+The fundamental idea of the research question was to \textit{investigate how the home environment of the university student has changed to accommodate full-time study under the restrictions of the COVID-19 pandemic}.
+In order to answer this main research question, it was broken down into two more concrete secondary research questions, which would explore \textit{how the location of the study area has changed}, as well as \textit{how the equipment of the study area has changed}.
 
 \subsection{Methodologies}
-In order to perform their research as best as possible, the authors have decided on utilizing three separate methodologies in order to achieve a coherent approach and take into account as many aspects related towards \emph{study environments} as possible.
-They started by performing auto-ethnography upon themselves to have an introspective look over their own experience during the first and second semesters of their studies within the context of the pandemic restrictions.
-Using the findings of the auto-ethnography, they have arrived at a number of interview questions that where used in a series of semi-structured interviews with participants outside of the research team.
-Ending by performing an photographic ethnography of pictures taken by the same interview participants in order to analyse them in parallel with the interview transcriptions and achieve a more coherent image of each participants actual study environments.
+In order to perform the research as best as possible, we decided on utilizing three separate methodologies in order to achieve a coherent approach and take into account various aspects related to the \emph{study environment}.
+We started by performing auto-ethnography upon ourselves to have an introspective look over our own experience during the first and second semesters of our studies within the context of the pandemic restrictions.
+Using the findings of the auto-ethnography, we arrived at a number of interview questions that where used in a series of semi-structured interviews with participants outside of the research team.
+Lastly by performing a photographic ethnography of the pictures taken by the same interview participants in order to analyse them in parallel with the interview transcriptions, a more coherent image of each participants' actual study environments is achieved.
+The following sections will explain which methods are used and our overall methodological strategy.
 
@@
 
-Before starting the auto-ethnography research, each researcher has been given an information sheet and consent form which had to be sign by the research-participant and one of the other researchers.
-The structure of the document has been agreed upon unanimously by the team as so to avoid any potential issues related to data privacy of the resulting documents from the auto-ethnographic research.
+The research began with the auto-ethnography \cite{adams_ellis_jones_2017, dighe_joshi_2014} approach.
+Each researcher conducted an inner-inquiry upon their experience that resulted from the drastic change to full-time distance learning, as well as making a comparison between their study/work environment and their study workload between previous semesters.
 
-After signing the consent form, each researcher has had to conduct an inner-inquiry upon his or hers experience that resulted from the drastic change towards full-time studying from home, as well as making a comparison between their study/work environment and study workload between their previous semester (e.g.
-Winter 2019/2020) and the next restricted semesters (e.g.
-Summer 2020, Winter 2020/2021).
-
-Upon finishing their report about their own experience, each researcher had to take a picture of their current study environment/s (see Figure~\ref{fig:figure1} as an example) and attach it to the report.
-Afterwards all reports where analysed by each researcher, and researcher-participant had to perform a presentation of their experience to all other researchers.
-Findings culminating in organizing the information using thematic analysis using Miro\footnote{\url{https://miro.com/}} and extracting possible interview questions for their findings.
-After having decided on the possible interview questions, sample semi-structured interview took place, having one of the researchers as a participant, and two others as interviewer and observer.
-Upon finishing the sample interview, the interview question had been filtered to only five central questions as so to provide a structure for the incoming participant interviews.
+Upon finishing our reports on our own experience, each researcher had to take a photograph of their current study environment (see Figure~\ref{fig:figure1} as an example) and attach it to their report.
+Afterwards all reports where analysed by each researcher and the researcher-participant had to present their experience to the team.
+The information was then analysed using \emph{thematic analysis} within \emph{Miro}\footnote{\url{https://miro.com}} so as to extract possible interview questions for later use.
+After having decided on the possible interview questions, a practice semi-structured interview took place, with one of the researchers as a participant, and two others as interviewer and observer.
+Upon finishing the sample interview, the interview questions were refined down to five central questions that were used as a guide for the participant interviews.
 \begin{figure}
 \centering
-  \includegraphics[width=0.9\columnwidth]{figures/auto-e-picture}
-  \caption{Sample picture from the Auto-Ethnographic method, showing the desk of one of the researchers}~\label{fig:figure1}
+  \includegraphics[width=1\columnwidth]{figures/auto-ethnography.JPG}
+  \caption{Sample photograph from the auto-ethnographic method, showing the desk of one of the researchers}~\label{fig:figure1}
+\end{figure}
+
+\begin{figure}
+\centering
+  \includegraphics[width=1\columnwidth]{figures/auto-ethnography-annotated.JPG}
+  \caption{Applying annotation to the same photograph as shown in Figure \ref{fig:figure1}}~\label{fig:figure2}
 \end{figure}
@@
 \subsubsection{Semi-structured Interviews}
-The 5 interview questions
-Who were the participants (general information), where the interviews were taken, how we found the participants, age, academic status, consent management, tools, analysing the interview, miro idea board / extracting data THEMATIC ANALYSING
+Semi-structured interviews\cite{adams_2015} were conducted to gather more information on how the home studying environment had changed for a variety of students.
+We opted for this more open style of information gathering because of the diverse variety of possible living situations.
 
-Some people did not know how the pandemic will evolve so they did not prepare for a long home learning situation, we asked them how the ideal setup will look like or if they know the next semesters  will be remotely what will they change.
+Our participants were friends and colleagues from varying backgrounds, countries, universities, and degree programs.
+An overview of their basic information is shown in Table \ref{tab:table1}.
+Using our interview questions as a guide to prompt a discussion on a specific point of interest, the semi-structured format allowed us to ask follow-up questions to further explore the participants' unique situations.
+These details may not have been captured in a more strictly structured interview or by a survey.
 
-issues: Single interviewer, no observer., subjectivity issues due to the participants being friends
+The topics that guided our interview questions centered on the home and study-area environment.
+First we asked questions to determine their current student and work status in order to get an idea for how heavy their work-loads were.
+This helped us understand how intensely they use their home office, and how important it is for their work and studies.
+We also asked questions about their living situations to understand how they might deal with issues of privacy, noise or other distractions, and sharing study-spaces with cohabitants.
+We then asked about their study-area and immediate surroundings.
+This gave us a picture of their immediate study environment; what equipment they use and how they use the space.
+We also asked them to think about the semester before the pandemic, and to reflect upon any changes they made to their study areas since transitioning to full-time distance learning.
+This includes rearranging furniture, purchasing or upgrading new equipment, or using old things in new ways.
+We then asked about any issues or challenges present in their current studying environment.
+Finally we asked them to imagine their ideal study area, and to share any improvements or "wish-list" items they would like if they could change anything and afford to do so.
+\begin{table}
+  \centering
+  \begin{tabular}{l l l l}
+    % \toprule
+    & & \multicolumn{2}{c}{\small} \\
+    \cmidrule(r){1-4}
+    {\small\textit{ID}}
+    & {\small \textit{Academic Program}}
+      & {\small \textit{Living Space}}
+    & {\small \textit{Study Space}} \\
+    \midrule
+    P1 & Bio-Med Engineering & Shared Apt. & Bedroom \\
+    P2 & Interaction Design & On-Campus & Shared Dorm \\
+    P3 & Mechatronics & On-Campus & Shared Dorm \\
+    P4 & Physics & Shared Apt. & Bedroom \\
+    P5 & Data Science & Shared Apt. & Bedroom \\
+    P6 & PhD Law & Apartment & Living-room \\
+    P7 & Data Science & With Parents & Bedroom \\
+    P8 & Artificial Intelligence & With Parents & Bedroom \\
+    % \bottomrule
+  \end{tabular}
+  \caption{A variety of living and studying situations}~\label{tab:table1}
+\end{table}
+
+The participants were invited to take part in a short interview of approximately 30 minutes to discuss their current home studying environment, and to compare it with a semester before the pandemic.
+They were given information sheets and consent forms, informing them that their identities would remain anonymous to all but the interviewer and the consent form manager.
+They were also asked to provide a photograph of their studying area for photographic ethnography.
+
+To avoid risk of COVID-19 exposure to both participant and researcher, all interviews were conducted via video conferencing and recorded with consent from the participant.
+The researcher then transcribed the recordings using \emph{Temi}\footnote{\url{https://www.temi.com}}.
+The transcriptions were finally anonymized and shared with the team for analysis.
+We then applied thematic analysis to the content of the transcripts on a shared Miro board.
+The themes and patterns that emerged are discussed in the Findings section.
 
 \subsubsection{Photographic Ethnography}
-Using the photo analysis method, the researches wanted to discover the study setups of students engaged in distance learning.
-The method was chose to give a better overview of essential items used by students for improving the health and comfort during online studies, at home.
-The participants agreed on sending a photo of their environment before the semi-structured online interviews.
-Moreover, the researchers shared photos of their personal setups used for remote studies.
-Two consents were used in the research: one sent to the participants before the semi-structured online interview, and another, for the researchers themselves, before starting the auto-ethnography process.
-The processes of storing, analyzing, anonymizing and deletion of the participants and researchers photos were covered in the mentioned consents.
+Using the photographic ethnography method, we attempted to study the home study spaces of participants in more detail.
+The method was chosen in order to give a better overview of essential items used by students for improving their health and comfort during online studies at home.
+The participants agreed on sending a photograph of their study environment before the semi-structured online interviews in a email to the researcher who provided the consent forms.
+Moreover, the photographs of the researchers' personal setups, provided in the auto-ethnography phase, were also analyzed.
+The processes of storing, analyzing, anonymizing, and deleting the participants' and researchers' photographs were covered in the consent forms signed for the semi-structured online interviews and for auto-ethnography.
 
-As visual recording of the personal space …, not all the participants agreed to expose their working space.
-A number of X photos was collected in the photo analysis process.
-A visual difference between the state of the learning environment before and after switching to distance learning could not been made, as the photos received by the researchers were taken in the actual context of the pandemic.
-Only one participant sent photos of their old and their actual setup.
-One participant sent a photo of their current setup, and two photos of setups that could serve as inspiration for their ideal setup.
-All photos received by the participants were used in the analyze process.
+As visual recording of one's personal space can be considered a breach of privacy.
+Not all the participants agreed to photograph their study areas.
+In all, 21 photographs were collected in the photograph ethnography process.
+Some participants sent multiple photographs of their desk from different perspectives.
+A visual comparison between the state of the learning environment before and after switching to distance learning could not be made, as the photographs received were taken in the current context of the pandemic.
+One participant sent a photograph of their current setup, and two pictures of their ideal study space that could serve as inspiration for their future office arrangement (see Figure~\ref{fig:figure3}\cite{instagram_2019}).
+All photographs received by the participants were used in the analysis process.
+
+The photographic ethnography method was used as an independent method to make a classification of the items used by students in the distance learning process, but also as a complementary method for the semi-structured interviews, to help us in having a more clear visualization of the environments of the participants.
+After collecting and anonymizing all the visual data, we arranged the photographs in Miro by a color and number code scheme.
+Every photograph would have the same number and color as the interview notes, which made sure we analyzed the transcripts of the corresponding photographs.
+This method of classification was used to offer a better correlation between the described environment and the representative photograph.
+
+For an easier understanding of one's home study area, the photographs sent by us were completed with short annotations on objects present in the image (see Figure \ref{fig:figure2}).
+Each note summarized what the specific object is, what it is used for, and how it improves the quality or efficiency of the distance learning process.
 
@@
 \centering
-  \includegraphics[width=0.9\columnwidth]{figures/perfect-setup}
-  \caption{A sample photo from the Photographic Ethnography method given by one of the participants, it is the desired "perfect study environment''}~\label{fig:figure1}
+  \includegraphics[width=1\columnwidth]{figures/perfect-setup}
+  \caption{A sample picture from the Photographic Ethnography method given by one of the participants; it shows the desired \emph{perfect study environment}}~\label{fig:figure3}
 \end{figure}
@@
 
-We need to talk about the research question results here.
+\subsection{Auto-ethnography}
+Every researcher that took part in the auto-ethnographic process is currently taking part in distance learning, differing in degree program and the number of credits per semester.
+Some researchers admitted to registering for more courses this semester than in a typical, on-campus semester.
+The rationale was that commuting to the university is no longer required, and activities outside the house are restricted by the current regulations, which frees up more time for coursework.
+One participant admits that they overestimated the extra time that could be gained from not commuting, traveling, or taking part in social activities.
+Every researcher had to implement changes in their everyday schedule and their way of working on group projects or individual assignments, in order to respect the regulations in place caused by the pandemic:
 
-Our findings from the interviews
+\begin{quote}
+\emph{All the projects I was doing at home, inviting colleagues over, at their place or in a coffee place. Now all the meetings are remote.}
+\end{quote}
 
-Our findings from the photos: Both participants and from the auto-ethnography
+All researchers made changes to their home study setup.
+One participant who received an ergonomic desk and an additional monitor from their employer focused more on improving the room aesthetics, decorating with plants and drawings, and painting their wall.
+They mentioned that creating a comfortable, cozy place improves efficiency during working time.
+Another participant changed the location of their study area from a common room to a guest room that is no longer being used due to the restrictions.
+This change in location was to avoid being disturbed in the common room.
 
-The analyze of the photos received from the participants and from the researchers involved in the study, showed unique, personalized study environments,  with a commune focus on ergonomics, efficiency and aesthetics.
-The result showed that the position of the working desk is usually located close to a direct source of natural light.
-The importance of a natural source of light was mentioned by several participants during the semi-structured online interview process.
-Items such as: second screen, laptop, lamp, plants, notebooks were …
+All researchers want to improve their current study area as the distance learning may extend into the future.
+Common items that are desired for creating a more effective study space are ergonomic chairs, adjustable height desks, better headsets, second monitors, desk lamps, or even separate working/studying places at home.
+
+\subsection{Semi-structured Interviews}
+After transcribing the recorded interviews, we read each-others' transcripts and analysed them.
+Using thematic analysis we identified some emerging themes.
+The most common themes were disruptions and annoyances in the home, complaints about poor ergonomics that resulted in pain, the importance of lighting, and strategies to maintain focus and motivation.
+
+We found that all but one student made changes or improvements to their home study environment.
+This student still attends lectures on-campus, but at reduced capacity.
+The frequency with which they study at home has not notably increased since the pandemic.
+Equipment upgrades included purchasing a printer and scanner, improving lighting, new headsets or noise-cancelling headphones, a laptop stand, a power strip, new house plants, and lumbar support to prevent back pain.
+Some changes that did not require spending any money include moving furniture to create a more separate dedicated study area, moving desks closer to a window for better lighting, and using a whiteboard that went previously unused.
+
+We found that even if sharing a home with other people, most participants now have a dedicated study area where they can be alone, where before they had to share their study space with others or study in a common area.
+The exception are the students who live on-campus in a dormitory.
+
+In most cases the desk and study area is in the bedroom.
+This combination of study and sleeping space was sometimes a problem for some participants.
+One participant said it was difficult to take breaks and relax because they were surrounded by reminders of work, where when they were attending lectures on-campus there was enough of a separation to make the switch mentally.
+Some students combat this by making a point to do all school-related work only at the desk, where before they might have done some studying on the couch, in a chair, or in bed.
+
+Some people were initially reluctant to make changes or invest money because of the uncertainty about how long the pandemic restrictions will remain in effect.
+At the time of this writing, we are currently in our second distance learning semester.
+While most of the changes discussed by our participants were enacted in their first pandemic semester, some larger purchases finally were made during the second pandemic semester.
+
+Lastly we asked how their ideal setup would look like if they could make further changes or investments.
+The most common ``wish-list'' item was a more comfortable chair.
+Students are spending sometimes over 12 hours in their chairs.
+Reports of back pain were the most common complaint among our interviewees.
+
+\subsection{Photographic Ethnography}
+We analyzed 11 sets of photographs both from the participants involved in the interview and from ourselves.
+We found that every student has a dedicated study setup place at home, arranged to meet the everyday needs for distance learning in the current situation of the pandemic.
+Every setup has a dedicated study desk, a chair, a laptop and ornamental items arranged on or around the desk.
+The ornaments were personal photos, trophies, flags, drawings or Christmas decorations.
+We classified those items that are present in every setup as “indispensable items”.
+Other relevant items, that were present in most of the study environments of our participants were lamps or any other source of artificial lighting, decorative plants on or near the desk, storage boxes or drawers containing books or other learning related supplies, second screens, pencils and paper used for writings, and headphones or speakers.
+We observed that the participants who do not have a good ergonomic chair use pillows to support the back while sitting.
+One of the photographs shows a setup with a chair and a professional lumbar support.
+We categorized those items as “items present in most of the study environments”.
+Items that were present only in one or two of the analyzed study spaces consisted of additional equipment that can improve productivity, such as an iPad or a scanner, but mostly related to the students' hobbies or particular academic area of interest: Raspberry Pi board connected to diverse sensors, gaming console, electronics used for personal projects, or painting brushes.
+Another finding consists in a small number of participants who use two laptops.
+This can be used to separate academic studies from work related activities.
+For example, one participant used one laptop for notes and the other for work, or to record one lecture for later watching while simultaneously attending another.
+
+One participant submitted two photographs of their ideal home study environment, that they may use as inspiration.
+Large desks with an artificial sources of light are presented.
+One setup is focusing more on technical equipment as it pictures a desktop for gaming, three monitors, and different controllers for a Nintendo console.
+The rooms are decorated in different styles; one with comics, books, portraits of fictional characters and figurines, and another in a more simple aesthetic focusing on objects like books, electronics like a Raspberry Pi board, small plants, inspiring framed quotes on the wall, and a warm blanket on the chair (See Figure 3).
 
@@
 
-Things to talk about: 
-1.Universities could open libraries or study spaces. Even increase the amount of space post-pandemic, as an issue already existed
-2. Items that are we recommend to use for study and the uni should give discounts to
-3.
+The following section will discuss the findings achieved and analyze them from different perspectives. Each subheading explains the type of perspective being discussed.
 
-\subsection{Limitations}
+\subsection{Biases in Participation}
+%Not used
+\begin{comment}
+There was an obvious variation in the results we achieved.
+It is therefore feasible to discuss what the research results would have looked like if the number of participants had been higher, or if the participants had studied other educational disciplines.
+Most of the participants were students at the Vienna University of Technology in Austria, which is a delimitation.
+Overall, We felt that the wide variety of situations among these students would help us identify many different types of problems and solutions.
+\end{comment}
 
-\section{Implications for design}
+Upon closer look within the participants' characteristics, it must be noted that our “sample” is not very diverse from a geographical point of view.
+All participants, including ourselves, live and study either in Austria or another EU member country.
+In terms of education level, only Bachelors, Masters, and PhD students have participated, no lower education.
+The degrees have been mostly IT or science related, from Vienna University of Technology or other European universities, as well as Erasmus students in Vienna.
 
-It is worth noting that the research presented within this paper is not meant necessarily to provide the HCI community with a new form of interaction or a profoundly new methodological approach in how human-computer interaction can be studied, but it is meant to be seen more through the lens of \cite{dourish_implications_2006} where the significance of \emph{``Implications for design''} stems from observing human habits within a highly isolated scenario where most of the study and work interactions are perpetuated solely through technology.
-The authors desire is not to emphasize the need for bigger screens, or more comfortable chairs, but to show how much of our lives \emph{can} be replaced through software.
+An important bias that had occurred within our interviews is due to the already existing relationships between us and the interview participants, as well as the decision of not utilizing the classical interviewer and observer technique due to time constraints as well as to avoid causing discomfort towards the participants in discussing their lives with an unknown person in the interview.
+It is also possible to consider in what way our prejudices have affected the results achieved.
+This remains uncertain but can be observed by discussing the results objectively.
 
-\subsection{Office of the next pandemic}
+One of the participants in the study also participated in a hybrid semester, which differs from the other participants' situations.
+A hybrid semester means that the practical laboratories take place at the university on-site, while still following social distance measures.
+The participant mentioned that the mixture of having access to the university's resources, having regular social interaction but also maintaining the flexibility and benefits of studying from home during certain weekdays, is a perfect balance between academic and private life.
+We therefore want to emphasize the strength of being able to carry out studies with a hybrid solution.
+The student can then carry out pandemic-safe studies even if parts of the curriculum take place on campus, precisely because the campus is not fully occupied.
 
-Given our interviews with the participants, no clear generalizing statement can be drawn on previous study setups possessed before the enactment of social distancing norms.
-But several have attributed a more aware understanding of the need to have such an environment within their homes.
-Noticing the likely-hood of our current situation to continue for at least one more semester, multiple participants had come to the conclusion and indeed already have plans of improving their study and work environments.
-Putting in question if a need in providing highly economical solutions in so as to reduce the overall cost of creating such a setup might be the next and most valuable step for the industry to take.
+\subsection{Motivation}
+While the discussion topics focused mainly on the physical space, equipment, and devices used by the students to facilitate effective learning, some students mentioned that the new restrictions have challenged their motivation and mental health.
+Some of the coping strategies shared by our interviewees include moving the desk closer to a window to increase natural lighting and allow them to look outside, setting houseplants around their work-space, distinguishing between work and relaxation time by doing school related work strictly at the desk, and connecting with friends or colleagues on a video chat left on in the background for the effect of having company.
 
-\subsection{Replacement of social interaction}
+Regardless of the participants' backgrounds a trend of declining motivation emerged in the research, larger than expected.
+All participants referred several times during the interviews to observations that they experienced a deteriorating level of motivation despite the fact that we did not ask any semi-structured question about motivation.
+Motivation can therefore be seen as a rising and hidden problem even if the students' home office studies or home office equipment worked well.
+We want to attribute the deteriorating motivation to the prevailing pandemic that forces students to study from home and be isolated from the campus life.
+What the challenges could entail varied depending on the participants.
+Two participants clearly stated that they did not appreciate studying without their classmates.
+One student was missing the sunlight and feeling of freedom.
+Another student found it difficult to focus on the computer screen for eight hours, but had no big challenges studying remotely.
 
-Multiple participants have expressed an inner desired to talk about their motivational issues while studying in this new environment.
-And to our amazement, different solutions in coping have been applied by each, from simple \emph{Zoom} study meetups, to arguably illegal (though depending on the country, might not be) face-to-face lecture viewings.
-Here the authors would like to express that a proper replacement of the in-class lecture experience, still does not exist and some participants have even emphasized a small regress due to the constant gap in interactivity that distance learning cannot overcome.
+We also saw a pattern that the participants' motivation was stronger in the first semester of the pandemic (2020 Summer) compared with the second semester of the pandemic (2020 Winter).
+We believe this can be attributed to society’s initial ignorance in the early pandemic, and that people primarily thought the early lockdown situation would not last for long.
+We therefore claim that the students' motivation was slightly better during the first semester because they kept their spirits up.
+This allowed the students to complete their studies in a distance learning format during the first semester of the pandemic without being too negatively affected.
 
-\section{Conclusions and future work}
+\subsection{Equipment}
+This initial ignorance to how long the restrictions would last can also be seen as an argument as to why six out of eight participants acquired new technical equipment in the middle of the pandemic, when it was more obvious that distance learning would continue.
+Upgrading the home office was eventually considered a necessity when the students realized that distance-learning would remain.
+The technical equipment that was most commonly bought among the participants were extra monitors, touch-pads, printers, headphones and mouses.
+However, we argue that it is still difficult to generalize what type of technical equipment students need to add in their home office setup due to the fact that the setup differs greatly by situation.
+We note that none of the participants needed to buy a computer to be able to transform into the distance learning format.
+We believe that this is due to the fact that university studies were already digitized to a large extent before the pandemic broke out.
+Consequently, switching to full-time distance learning was not too painful even though motivation was strongly negatively affected.
+As the technical equipment is central to distance learning, we believe that students in general have chosen to prioritize a decent set-up.
+We believe that many students prioritize buying the most relevant technical equipment at the beginning of their university education.
+However, we believe that most students needed to update some of the technical equipment.
+Only one of nine participants, for example, did not buy any extra electrical equipment in 2020.
+A short conclusion is therefore that most home offices were not optimized for distance learning at the beginning of the pandemic and that many students have had to upgrade their equipment successively.
 
-1. A study on a more diverse group of students
-2. A more in-depth study about motivational aspects
-3. West country rich 
-4. Didn’t realize the length of the pandemic
-5. What could the regulations look like?
-6. Maybe (?) we have a OK demographic picture of the participants (students)
+\subsection{Health and Comfort}
+Studying in the home office sets a new level of understanding ergonomics in terms of basic office equipment.
+We would like to point out that there was dissatisfaction with the participants' office chairs, which most have described as being ``unergonomic''.
+The chairs were described as stiff, offered a bad working posture, or could not be adjusted in height.
+One of the participants, when upgrading their study space, mainly focused on the ergonomic aspects and bought items, such as lumbar support pillows, that can help with the severe back pain caused by the long hours spent at the desk.
+The participant also mentioned that they bought, after switching fully to distance work and studies, a pillow with memory form that can improve back posture during sleep.
+Back pain can also be attributed to the lack of mobility and exercise due to lockdown restrictions.
+We therefore believe that there may be persistent health issues if students do not choose to upgrade their furniture in the future home office.
+Studying at the university offers better ergonomics with chairs, benches and lamps that are adapted for long hours of studying.
+Consequently, five of the participants answered that they wanted to upgrade their chair if they could.
+Three of the participants also answered that they would prefer to have a separate office if they could, which was not possible without changing accommodation.
+We therefore believe that it is necessary for all students to reflect on their situation and be flexible and creative in how they can improve their home office.
+
+All students may need different solutions as situations always differ.
+We also believe that inappropriate routines that office equipment can generate are difficult to detect.
+It is easy to get used to equipment that works but is not optimal, or even hazardous.
+We therefore urge all students to reflect about their home office standard and how it could be improved.
+We consider it important to ask ``what do I need to improve if I am going to study here for another year?''.
+According to the research findings, all participants experienced a negative effect of ergonomics that affected their studies.
+Good lighting, fresh air, or working posture have been the main problems detected.
+Sitting still in one and the same room was considered a negative aspect of distance learning.
+Improving the study area as early as possible, we claim, will prevent easy to avoid health issues in the long run.
+
+Two of the participants also pointed out that their eyes ached in the evening, after hours in front of the computer.
+This can be avoided with regular breaks, blue light filtering software, or blue light filtering glasses.
+These participants did not consider or were not aware of these solutions.
+We believe that this is not because they do not want to improve their health, but because they do not prioritize the time to reflect on their home office setup.
+Moreover, the importance of a natural source of light was mentioned by several participants during the interview sessions.
+We would therefore like to encourage all higher education institutions to offer students a sort of tips and tricks manual based on existing research on ergonomics and other desk related comfort improvements in order to better prepare students towards distance learning and point their attention to this matter.
+
+\subsection{Financial Limitations}
+From the fact that the participants had difficulty answering questions about their ideal study setup, we argue that they had not processed their own thoughts about whether they could improve their home office or not.
+This indicates that ergonomics have been prioritized away in the hectic noise of distance learning, as well as due to financial limitations.
+While most of our participants also work, several do not, and one has actually had their job activity interrupted due to the ongoing pandemic restrictions.
+Financial limitations have halted their desire to improve their work environment further.
+Possible partnerships between educational institutions and retailers in order to provide offers and discounts for students could prove effective in cutting costs for the students and motivating them to purchase needed home-office equipment.
+This would in turn boost sales for retailers, providing a win-win solution.
+Another solution could be found from the already established furniture rental services that currently work with other companies in facilitating their move within cities like Vienna, by providing low to mid end study equipment for Erasmus students.
+
+\section{Implications for Design}
+
+It is worth noting that the research presented within this paper is not meant necessarily to provide the HCI community with a new form of interaction or a profoundly new methodological approach in how human-computer interaction can be studied, but it is meant to be seen more through the lens of \cite{dourish_implications_2006}, where the significance of \emph{``Implications for design''} stems from observing human habits within a highly isolated scenario where most of the study and work interaction is conducted solely through remote technology.
+We do not intend to emphasize the need for bigger screens or more comfortable chairs, but to show how much of our lives \emph{can} be replaced through software.
+
+\subsection{Office of the Next Pandemic}
+
+Given our interviews with the participants, no clear generalizing statement can be drawn on previous home-office setups possessed before the enactment of social distancing norms.
+But several have acquired a more acute understanding of the need to have a dedicated study environment within their households.
+Noticing the likely-hood that our current situation will continue for at least one more semester, multiple participants had come to the conclusion, and indeed have already made plans, of improving their study and work environments.
+This highlights two important aspects related to distance learning.
+
+The lack of awareness from most students about the importance of having a well equipped and personalized study environment to combat the imminent health issues that might appear from long term studying at home.
+For which we propose a small leaflet (see Figure~\ref{fig:figure4}), personalized for each educational institution, which contains small tips and tricks for creating such and environment at home.
+As well as an online platform where students can share advice between each other at all times, from how to better arrange their desk within their room to retailers which offer low prices for different study essentials.
+
+The increasing economical disadvantage that students might encounter due to the pandemic restrictions and the clear lack of student jobs available.
+For this we propose possible partnerships between educational institutions and furniture or study equipment retailers in order to provide discounts for students and so also increase potential sales for the involved retailers, creating a win-win situation for both parties.
+As seen within our research, Erasmus students suffer most from lack of equipment due to their studies being "temporary" and so heavy investing in accommodations is undesired.
+In this sort of situations, we have already observed existing companies in Vienna\cite{orr_2020} which rent furniture towards other companies/individuals in order to help them move.
+The same companies could offer low-to-mid furniture items for Erasmus students as well, at a lower price then buying, and so not only lessen the financial burden on students, but also create a reusable furniture market, avoiding unnecessary waste of resources.
+
+\begin{figure}
+\centering
+  \includegraphics[width=1\columnwidth]{figures/leaflet.png}
+  \caption{A sample informative leaflet created by our team in cooperation with Anna Scassillo}~\label{fig:figure4}
+\end{figure}
+
+\subsection{Replacement of Social interaction}
+
+Multiple participants have expressed an inner desire to talk about their motivational issues while studying in this new environment.
+We were impressed that different solutions for coping were applied by each participant, from simple \emph{Zoom} study sessions, to potentially illegal (depending on the country) group lecture viewings that broke social distancing restrictions.
+Issue is that even with these make-shift solutions, lectures, class presentations and general group work are still much harder to occur under social isolation and current technological solutions are heavily lacking.
+Although, there are current projects such as VReddo \cite{vreddo_2020} that try to overcome this problem in the educational sector by providing Virtual Reality classroom equipment and software.
+While a solution like this can be quite expensive, especially for a university such as Vienna University of Technology that has such a large number of students registered, we would argue that it could be used to improve diploma presentations or classes with a small number of students.
+
+Sadly, for now we would argue that there is no proper replacement for the in-class lecture experience, and most likely students will continue to feel a setback in their studies due to the continuous lack of interactivity that current IT solutions fail to overcome.
+
+\section{Conclusions and Future Work}
+
+This conference paper looked at the differences in students' study situations and at-home study spaces during the current pandemic of COVID-19.
+To protect society from the virus, the university has transformed teaching into a distance-adapted solution in the students' homes.
+This creates new challenges for all students, however, the challenges are different depending on their individual living situation.
+
+The research has shown that there is a deterioration in motivation due to the sustained distance learning.
+This places demands on students' inner motivation, which is a decisive factor in how the studies proceed.
+Although many students have good technical equipment in the form of computers and mobile phones with cameras, many students have nevertheless updated their equipment to some degree during the pandemic.
+As the individual circumstances of our participants' lives vary, it is not possible in this study to generalize the equipment gap, however, dual screens and touch-pads have been a prominent interest.
+We have identified simple changes a student could make to their at-home study environment that would improve the effectiveness of sustained distance-learning.
+Consequently, the university studies have a greater chance of success, despite the circumstances, as the students adapt to the new learning format.
+
+There is also a health risk that studies in the home office will cause ergonomic problems such as back pain, as the furniture in the home office may not offer the same comfort and support as the furniture at the university.
+There were also complaints of eye strain from inadequate lighting and from staring at a screen for too many hours.
+In many situations, the home office is in the same room as the student's bedroom.
+One solution is to move the desk closer to a window.
+This has the added benefit of helping the eyes rest as they focus on objects outside of the window, and to improve the student's mood and motivation.
+If this is not possible, a bright desk lamp or a standing lamp may be used.
+Additionally, if a student cannot afford a chair designed to support one for prolonged sitting, they can use lumbar supporting cushions as a backrest with their existing chair.
+
+As the pandemic experience influenced the way studies are carried out and brought with it a process of digitalization in the educational field, we believe that in the future a new alternative for studying may appear.
+A mix between having access to online courses and resources with the ability to join on-site laboratories and seminars, may offer more flexibility towards studies and may be a better solution for both students and teachers for organizing their schedule accordingly.
+Future research can be carried out focusing on the evolution of the environment at home in order to support the hybrid solution, and how having access to some of the university facilities and occasional social interaction can increase motivation.
+
+Future research on the motivation of students engaged in distance learning studies, but not in a context of a pandemic, would also represent a major interest.
+Social interaction and collaboration are important values developed in the academic life and they were severely affected by the current situation by the regulations that are in place in nearly every country.
+Therefore, a further study that focuses on the motivation of individuals performing distance learning, but without any restriction on their personal life and with the possibility of meeting outside the university campus, would bring value to understand the necessity of academic social life.
+
+Finally, we would like to point out that there is still a lack of awareness of how to carry out university studies in a distance-adapted format.
+According to our analysis, this has been overlooked due to the pandemic as well as the usual study workload that students have to complete.
+There are also financial reasons a student may not be able to create an "optimal" home-office.
+However, simple solutions can be found.
+We propose educational institutions to inform students about possible enhancements that they can implement in order to improve their home study environment.
 
 \section{Acknowledgments}
-Thank you to all our interview participants for taking their time off their studies and work in order to help us with this assignment.
-Thank you to TU Wien for giving us access to the needed tools in order to prepare the assignment,  \textit{as good as they are}.
-No other funding was provided.
+We thank all of our interview participants for taking the time from their studies and work in order to help us with this assignment.
+Thank you to Anna Scassillo for providing us with the amazing drawings used to create the informational leaflet.
+Thank you to Vienna University of Technology for giving us access to the needed tools in order to prepare this assignment, and of course to our supervisors for offering us guidance along the way.
 
@@
 \bibliographystyle{SIGCHI-Reference-Format}
-\bibliography{sample}
+\bibliography{references}
 
